\documentclass[letterpaper,10pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Custom font
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

%Items formatting
\setlist[itemize]{topsep=1pt}
% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}} \\
    \vspace{5pt}
    \small
    Ph: +1 (323) 334-7408 \quad Email: \href{mailto:jaijayes@usc.edu}{jaijayes@usc.edu} \\
    LinkedIn: \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9} \\
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------%
\section*{Education}
\textbf{University of Southern California (USC)}, Los Angeles, CA \hfill Aug 2024 -- May 2026 \\
\textit{Master of Science in Computer Engineering} \hfill GPA: 3.6/4.00 \\
Related Coursework: Computer Networks, Computer System Architecture, Advanced Computer Architecture, Algorithms, Database Management Systems, AI Agents.

\textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill April 2018 -- May 2022 \\
\textit{B.Tech. in Electronics and Communication (IoT and Sensors)} \hfill CGPA: 9.04 / 10.00 \\
Related Coursework: IoT Systems, IoT Edge Nodes, M2M Communication, Data Acquisition, MEMS and Nano Sensors, Advanced Microcontrollers.

%-----------SKILLS-----------%
\section*{Technical Skills}
\textbf{Languages:} Python, C, C++, Java, SQL, Verilog, Assembly, Embedded C. \\
\textbf{Hardware \& Wireless:} WiFi/BT Technologies, MQTT, Raspberry Pi, ESP8266, FPGA, UART, SPI, I2C. \\
\textbf{Cloud \& Automation:} AWS, Jenkins, Docker, Git, Linux, CLI, Testing Scripts, Postman, Wireshark. \\
\textbf{Web \& Frameworks:} Flask, HTML5, CSS3, JavaScript.

%-----------EXPERIENCE-----------%
\section*{Work Experience}
\textbf{University of Southern California}, Los Angeles, CA \hfill Jan 2025 -- Present \\
\textit{Teaching Assistant (EE 457) \& Course Producer (EE 354)}
\begin{itemize}
    \item Assisted Professor Puvvada in revamping assignments for Computer Systems Organization to improve learning outcomes.
    \item Held office hours and managed logistics for Intro to Digital Circuits, supporting student success in hardware concepts.
\end{itemize}

\textbf{USC MANN School of Pharmacy}, Los Angeles, CA \hfill May 2025 -- Present \\
\textit{Data Analyst}
\begin{itemize}
    \item Helped build and test custom CRM applications on Salesforce and created data visualizations on Tableau.
    \item Developed automation scripts to verify data integrity and streamline reporting processes.
\end{itemize}

\textbf{Accenture}, Bangalore, India \hfill July 2022 -- Aug 2024 \\
\textit{Backend Developer}
\begin{itemize}
    \item Spearheaded transition from manual deployments to CI/CD pipeline, reducing turnaround time by 50\% and streamlining Dev-QA handoffs.
    \item Developed and maintained custom CRM applications using Salesforce and APEX; delivered 30+ API services using MuleSoft.
    \item Recognized for exceptional performance with the Pinnacle TCI Award and Growth Catalyst Award.
\end{itemize}

\textbf{Schneider Electric}, Bangalore, India \hfill July 2021 -- Aug 2021 \\
\textit{Intern}
\begin{itemize}
    \item Researched UPS efficiency, proposing improvements for battery longevity and analyzing energy consumption trends.
\end{itemize}

%-----------PROJECTS-----------%
\section*{Projects}
\textbf{IoT-Based Keyless Bike Access System} \hfill 2019 \\
\textit{ESP8266, WiFi, Mobile App}
\begin{itemize}
    \item Developed a keyless authentication system using ESP8266 and WiFi for bike access via a mobile app.
    \item Implemented secure communication protocols to facilitate safe vehicle sharing.
\end{itemize}

\textbf{Smart Mirror with MQTT Home Automation} \hfill 2020--2021 \\
\textit{Raspberry Pi, ESP8266, MQTT}
\begin{itemize}
    \item Built a Smart Mirror integrated with home automation via MQTT to control appliances and display real-time info.
    \item Utilized Python scripts for data fetching and display logic on the Raspberry Pi.
\end{itemize}

\textbf{Web Scrapers and Automation Suite} \hfill 2018--Present \\
\textit{Python, Selenium, CLI, Testing Scripts}
\begin{itemize}
    \item Implemented Selenium-based test suites to verify feature deployment consistency across multiple user profiles.
    \item Developed CLI tools and testing scripts to automate routine data entry and validation tasks.
\end{itemize}

\textbf{Microarchitecture Design (EE 457 Course Project)} \hfill 2024 \\
\textit{Verilog, Questasim}
\begin{itemize}
    \item Designed and simulated single-cycle CPUs, ALUs, and Tomasulo machines using Verilog.
    \item Implemented hazard detection, forwarding units, and out-of-order execution logic.
\end{itemize}

\textbf{TCP/IP Socket Programming} \hfill 2025 \\
\textit{Python, Networking}
\begin{itemize}
    \item Designed and implemented client-server systems for data packet exchange using Python TCP/IP sockets.
\end{itemize}

%-----------CERTIFICATIONS & AWARDS-----------%
\section*{Certifications \& Awards}
\begin{itemize} \itemsep -2pt
    \item \textbf{MuleSoft Certified Developer (MCD - Level 1)} -- Certified 2023
    \item \textbf{Awards (Accenture):} Pinnacle TCI Award (Top Performer), Growth Catalyst Award.
\end{itemize}

\end{document}
