\documentclass[letterpaper,10pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Custom font
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.85in}
\addtolength{\textheight}{1.7in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-15pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-6pt}]

%Items formatting
\setlist[itemize]{topsep=0pt, itemsep=0pt}
% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}} \\
    \vspace{1pt}
    \small
    Ph: +1 (323) 334-7408 \quad Email: \href{mailto:jaijayes@usc.edu}{jaijayes@usc.edu} \\
    LinkedIn: \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9} \\
    \vspace{-15pt}
\end{center}

%-----------EDUCATION-----------%
\section*{Education}
    \textbf{University of Southern California (USC)}, Los Angeles, CA \hfill Aug 2024 -- May 2026 \\
    \textit{Master of Science in Computer Engineering} \hfill GPA: 3.7/4.00 \\
    Relevant Coursework: Advanced Computer Architecture, Computer Networks, Algorithms, AI Agents, Digital Circuits. \\

    \vspace{1pt}
    \textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill April 2018 -- May 2022 \\
    \textit{B.Tech. in Electronics and Communication} \hfill CGPA: 9.04 / 10.00 \\
    Relevant Coursework: Embedded Systems, IoT Systems, Cloud Computing, Object Oriented Programming.

%-----------SKILLS-----------%
\section*{Technical Skills}
    \textbf{Languages:} Python, C, C++, Swift, Verilog, Embedded C, Assembly, SQL, JavaScript, HTML5 \\
    \textbf{Hardware \& Embedded:} FPGA Design, SoC, WiFi, Bluetooth, Raspberry Pi, ESP8266, Sensors, Questasim, Quartus II, Multisim \\
    \textbf{Test Equipment \& Connectivity:} Oscilloscope, Logic Analyzer, MQTT, Wireshark \\
    \textbf{Cloud \& DevOps:} AWS (CodePipeline, CodeBuild, Stacks), CI/CD, GitHub Actions, JIRA, Linux, Git \\
    \textbf{Concepts:} Computer Architecture, Digital Logic, SDLC, Agile, Data Structures \& Algorithms

%-----------EXPERIENCE-----------%
\section*{Work Experience}
    \textbf{University of Southern California}, Los Angeles, CA \hfill Aug 2025 -- Jan 2026 \\
    \textit{Course Producer, EE354 (Intro to Digital Circuits)}
    \begin{itemize}[leftmargin=*]
        \item Assisted Professor Gandhi in teaching digital logic design, FPGA programming, and hardware verification using Verilog.
        \item Held office hours to debug student code and hardware issues, ensuring successful project completion.
        \item Managed logistics and graded assignments/exams focused on digital systems and Verilog coding.
    \end{itemize}

    \textbf{Accenture}, Bangalore, India \hfill July 2022 -- Aug 2024 \\
    \textit{Advanced Application Developer}
    \begin{itemize}[leftmargin=*]
        \item Supervised transition from manual deployments to CI/CD pipeline, reducing turnaround time by 50\% and improving release reliability.
        \item Developed and maintained custom CRM applications and API services, ensuring robust integration and performance.
        \item Created reusable frameworks for logging and error handling, enhancing system stability and debuggability.
        \item Collaborated with cross-functional teams to implement scalable solutions and resolve critical defects.
    \end{itemize}

    \textbf{Schneider Electric}, Bangalore, India \hfill July 2021 -- Aug 2021 \\
    \textit{Intern}
    \begin{itemize}[leftmargin=*]
        \item Researched UPS efficiency, proposing improvements for battery longevity and analyzing energy consumption trends.
    \end{itemize}

%-----------RESEARCH-----------%
\section*{Research}
    \textbf{Learning Optimal Gateway Placement for Low-cost Smart Cities} \hfill USC, 2025
    \begin{itemize}[leftmargin=*]
        \item Enhanced placement methodologies and created simulations to realistically model real-world scenarios.
        \item Presented poster at 14th Annual Electrical Engineering Research Festival, USC.
    \end{itemize}

    \vspace{-2pt}
    \textbf{OpenCV-Based AI-Driven Customer Screening System} \hfill Springer Journal, 2024
    \begin{itemize}[leftmargin=*]
        \item Developed an AI-vision powered system for crowd management using OpenCV \& Machine Learning.
        \item Published findings in \textit{Wireless Personal Communications}, DOI: 10.1007/s11277-024-11286-x.
    \end{itemize}

%-----------PROJECTS-----------%
\section*{Projects}
    \textbf{Microarchitecture Design (EE 457)} \hfill Verilog, FPGA, Computer Architecture
    \begin{itemize}[leftmargin=*]
        \item Designed and simulated single-cycle CPUs, ALUs, and Tomasulo machines using Verilog and Questasim.
        \item Implemented advanced concepts including register renaming, hazard detection, and out-of-order execution, verifying functionality through rigorous simulation.
    \end{itemize}

    \vspace{-2pt}
    \textbf{Alarm Clock on FPGA} \hfill Verilog, FPGA, Hardware
    \begin{itemize}[leftmargin=*]
        \item Built a fully functional alarm clock using Verilog on FPGA hardware.
        \item Managed display logic, clock cycles, and user input interfaces directly on the hardware platform.
    \end{itemize}

    \vspace{-2pt}
    \textbf{Smart Mirror with MQTT Home Automation} \hfill IoT, Raspberry Pi, MQTT, WiFi
    \begin{itemize}[leftmargin=*]
        \item Built a Smart Mirror using Raspberry Pi and ESP8266, integrated with home automation via MQTT over WiFi.
        \item Enabled control of appliances and display of real-time information, demonstrating seamless hardware-software integration.
    \end{itemize}

    \vspace{-2pt}
    \textbf{IoT-Based Keyless Bike Access System} \hfill ESP8266, WiFi, Embedded C
    \begin{itemize}[leftmargin=*]
        \item Developed a keyless authentication system using ESP8266 and WiFi for bike access via a mobile app.
        \item Facilitated secure vehicle sharing and demonstrated proficiency in embedded systems and wireless protocols.
    \end{itemize}

%-----------CERTIFICATIONS & AWARDS-----------%
\section*{Certifications \& Awards}
    \begin{itemize}[leftmargin=*] \itemsep -2pt
        \item \textbf{MuleSoft Certified Developer (MCD - Level 1)} -- Certified 2023
        \item \textbf{Pinnacle TCI Award (Accenture):} Recognized for exceptional performance (Aug 2023).
        \item \textbf{Growth Catalyst Award (Accenture):} Awarded for outstanding contributions in growth initiatives (June 2023).
        \item \textbf{National Cyber Olympiad (SOF):} Achieved Zonal Rank 1 in 2015 \& 2016.
    \end{itemize}

\end{document}
