\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome5}


\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}


% Custom font
\usepackage{mathptmx}


% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{1in}

\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule\vspace{-6pt}]

%Items formatting
\setlist[itemize]{
    leftmargin=2.5em,
    itemsep=2pt,
    topsep=0pt,        % removes space above list
    partopsep=0pt,     % removes extra paragraph spacing
    parsep=0pt         % removes spacing inside items
}

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}}\\
    {\normalsize Software Engineer \textbar\ Backend \& Distributed Systems}\\
    \small
    \faEnvelope\ \href{mailto:jaishah.work@gmail.com}{jaishah.work@gmail.com}
    \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9}
\end{center}
\vspace{-13pt}


%-----------EDUCATION-----------%
\section*{Education}
\textbf{University of Southern California (USC)}, Los Angeles, CA \hfill Aug 2024 -- May 2026 \\
\textit{Master of Science in Computer Engineering} \hfill GPA: 3.7/4.00 \\
\textbf{Relevant Coursework:} AI Agents, Distributed Systems, Database Management Systems, Algorithms.

\vspace{3pt}
\textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill April 2018 -- May 2022 \\
\textit{B.Tech. in Electronics and Communication} \hfill CGPA: 9.04 / 10.00 \\
\textbf{Relevant Coursework:} Web Technologies, Cloud Computing, Object Oriented Programming, Data Acquisition.

%-----------SKILLS-----------%
\section*{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    {\item{
     \textbf{Languages}{: Python, SQL, JavaScript, HTML5, CSS3, Java, C++, Django, ES6+} \\
     \textbf{Cloud \& DevOps}{: AWS (CodePipeline, CodeBuild), CI/CD pipelines, Docker, PostgreSQL, Heroku} \\
     \textbf{Frameworks \& AI}{: React, Node.js, Flask, RESTful APIs, LLMs, AI Agents, Machine Learning, OpenCV, CareKit}
    }}
\end{itemize}

%-----------EXPERIENCE-----------%
\section*{Work Experience}

\textbf{University of Southern California} \textbar\ \textit{Data Analyst} \hfill May 2025 -- Present
\begin{itemize} \itemsep -2pt
    \item Automated validation and testing using \textbf{Python} and LLM-driven scripts, processing \textbf{100,000+ records} and reducing manual reporting by \textbf{15 hours/week}.
    \item Developed \textbf{Tableau + SQL analytics solutions} to transform large-scale datasets into actionable insights, deploying dashboards to on-premise \textbf{Tableau Server} for organization-wide access.
    \item Engineered \textbf{data processing and ETL-style workflows} including cleaning, transformation, and relational joins to support accurate reporting pipelines.
\end{itemize}

\textbf{Accenture} \textbar\ \textit{Software Engineer} \hfill July 2022 -- Aug 2024
\begin{itemize} \itemsep -2pt
    \item Built and scaled \textbf{30+ RESTful microservices and APIs} supporting backend system design for \textbf{10k+ daily transactions}, improving distributed system integration, scalability, and production reliability.
    \item Designed and deployed automated \textbf{CI/CD pipelines} using \textbf{GitHub Actions} and \textbf{AWS CodePipeline}, reducing release turnaround time by \textbf{70\%} and enabling reliable continuous delivery.
    \item Defined API architecture with \textbf{OpenAPI 3.0} and implemented centralized \textbf{error handling and fault-tolerance}, reducing debugging time by \textbf{40\%}.
    \item Worked in an \textbf{Agile engineering environment} following structured development, validation, and release workflows.
\end{itemize}

\textbf{University of Southern California} \textbar\ \textit{Research Assistant} \hfill Aug 2025 -- Dec 2025
\begin{itemize} \itemsep -2pt
    \item Modeled \textbf{networked embedded systems} to evaluate gateway placement \textbf{strategies minimizing latency} and infrastructure cost under the guidance of \textbf{Dr. C. Baker}.
    \item Conducted simulation-driven architectural studies and presented findings at \textbf{USC’s Electrical Engineering Research Festival}.
\end{itemize}

%-----------PROJECTS-----------%
\section*{Projects}

\textbf{Healthcare \& Behavioral Insights App} \hfill \textit{2026} \\
\textit{iOS, CareKit, Docker, PostgreSQL, Heroku}
\begin{itemize} \itemsep -2pt
    \item Designed a longitudinal health-data analytics platform using CareKit to collect, store, and analyze patient-reported outcomes.
    \item Built containerized backend services with \textbf{Docker} and \textbf{PostgreSQL}, deploying to \textbf{Heroku} to enable scalable data persistence and secure health record management.
    \item Created interactive visualizations and feedback workflows to surface adherence trends, improving engagement by \textbf{25\%}.
\end{itemize}

\textbf{AadharVision} \hfill \textit{2021} \\
\textit{Python (Flask), OpenCV, REST APIs}
\begin{itemize} \itemsep -2pt
    \item Engineered a computer-vision–based access management platform using \textbf{Flask} to process real-time occupancy monitoring and identity validation.
    \item Implemented OCR and QR-driven verification pipelines integrated with external APIs, enabling automated authentication and compliance detection with \textbf{OpenCV}.
    \item Optimized backend request handling to support concurrent validation events with low-latency processing.
\end{itemize}

\textbf{Automated Google Form Submission Bot} \hfill \textit{2022} \\
\textit{Python (Flask), Web Automation}
\begin{itemize} \itemsep -2pt
    \item Designed an automation bot using \textbf{Python (Flask)} to bulk-fill Google Forms, optimizing time by \textbf{98\%} compared to manual entry before the era of AI agents.
\end{itemize}

\end{document}
