\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome5}


\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}


% Custom font
\usepackage{mathptmx}


% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{1in}

\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule\vspace{-6pt}]

%Items formatting
\setlist[itemize]{
    leftmargin=2.5em,
    itemsep=2pt,
    topsep=0pt,        % removes space above list
    partopsep=0pt,     % removes extra paragraph spacing
    parsep=0pt         % removes spacing inside items
}

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}}\\
    {\normalsize\scshape Software Engineer \textbar\ Full Stack \& Backend Systems}\\
    \small
    \faEnvelope\ \href{mailto:jaishah.work@gmail.com}{jaishah.work@gmail.com}
    \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9}
\end{center}
\vspace{-13pt}


%-----------EDUCATION-----------%
\section*{Education}
\textbf{University of Southern California (USC)}, Los Angeles, CA \hfill Aug 2024 -- May 2026 \\
\textit{Master of Science in Computer Engineering} \hfill GPA: 3.7/4.00 \\
\textbf{Relevant Coursework:} Database Management Systems, Computer Networks, Algorithms, Distributed Systems.

\vspace{3pt}
\textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill April 2018 -- May 2022 \\
\textit{B.Tech. in Electronics and Communication} \hfill CGPA: 9.04 / 10.00 \\
\textbf{Relevant Coursework:} Web Technologies, Object Oriented Programming, Cloud Computing.

%-----------SKILLS-----------%
\section*{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    {\item{
     \textbf{Languages}{: Java, SQL (T-SQL, MS-SQL Server), Python, JavaScript, HTML5, CSS3, C++} \\
     \textbf{Frameworks \& Data}{: Spring Boot, Hibernate ORM, Servlets, React, Node.js, PostgreSQL} \\
     \textbf{Concepts \& Architecture}{: SOAP/RESTful Web Services, Microservices, Agile/Scrum SDLC, Database Design} \\
     \textbf{Cloud \& DevOps}{: AWS (CodePipeline, CodeBuild), CI/CD pipelines, Docker, OpenAPI 3.0}
    }}
\end{itemize}

%-----------EXPERIENCE-----------%
\section*{Work Experience}

\textbf{Accenture} \textbar\ \textit{Software Engineer} \hfill July 2022 -- Aug 2024
\begin{itemize} \itemsep -2pt
    \item Built and scaled \textbf{30+ REST and SOAP microservices} using \textbf{Java Spring Boot}, supporting backend system design for \textbf{10k+ daily transactions} and improving distributed system integration.
    \item Developed robust data-tier frameworks using \textbf{Hibernate ORM} and \textbf{SQL/T-SQL} scripts to connect, query, and manage relational databases, significantly improving data retrieval and manipulation efficiency.
    \item Designed and deployed continuous \textbf{CI/CD pipelines} using \textbf{GitHub Actions} and \textbf{AWS CodePipeline}, reducing release turnaround time by \textbf{70\%} and enabling reliable Agile continuous delivery.
    \item Engineered centralized \textbf{error handling and fault-tolerance} logic across all services utilizing \textbf{OpenAPI}, directly reducing debugging and troubleshooting time by \textbf{40\%}.
    \item Actively collaborated in an \textbf{Agile/Scrum engineering environment}, taking part in rigorous SDLC processes, architecture design discussions, and updating data models based on framework requirements.
\end{itemize}

\textbf{University of Southern California} \textbar\ \textit{Data Analyst} \hfill May 2025 -- Present
\begin{itemize} \itemsep -2pt
    \item Engineered and modernized data processing architectures and ETL workflows via \textbf{Python} scripts, handling relational joins, cleaning, and transforming \textbf{100,000+ records} accurately.
\end{itemize}

%-----------PROJECTS-----------%
\section*{Projects}

\textbf{Healthcare \& Behavioral Insights App} \hfill \textit{2026} \\
\textit{Full Stack, Docker, PostgreSQL, Client/Server Models}
\begin{itemize} \itemsep -2pt
    \item Designed a full-stack longitudinal health-data platform utilizing client-server communication models to securely collect, store, and analyze structured patient-reported outcomes.
    \item Built containerized backend services integrated with \textbf{PostgreSQL} relational databases to persist scalable data, mitigating latency issues and proactively solving platform support constraints.
\end{itemize}

\textbf{AadharVision} \hfill \textit{2021} \\
\textit{Python (Flask), REST APIs, Relational Data}
\begin{itemize} \itemsep -2pt
    \item Engineered an access management platform driven by \textbf{REST APIs} to process responsive occupancy monitoring, securely verifying and authenticating individual identities.
    \item Implemented real-time integration workflows communicating with external credential verification APIs, troubleshooting bottlenecks to maintain low-latency concurrent processing.
\end{itemize}

\textbf{Web Scrapers and Automation Suite} \hfill \textit{2018--Present} \\
\textit{Automation, Testing Methodologies}
\begin{itemize} \itemsep -2pt
    \item Designed comprehensive testing suites to systematically simulate client workflows, thoroughly validating frontend and backend deployment consistency and improving software quality.
\end{itemize}

%-----------EXTRACURRICULAR-----------%
\section*{Extracurricular \& Workshops}
\begin{itemize} \itemsep -2pt
    \item \textbf{Conference:} Participant at POST/CON 2025, LA (June 4-5, 2025) -- Learned about AI-driven future of APIs.
    \item \textbf{Workshop:} Tableau Next Workshop (Oct 2, 2025) -- Hands-on demo of Tableau Next platform with inbuilt AI agents.
\end{itemize}

\end{document}
