\documentclass[letterpaper,10pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Custom font
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.85in}
\addtolength{\textheight}{1.7in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

%Items formatting
\setlist[itemize]{topsep=2pt, itemsep=1pt}
% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}} \\
    \vspace{4pt}
    \small
    Ph: +1 (323) 334-7408 \quad Email: \href{mailto:jaijayes@usc.edu}{jaijayes@usc.edu} \\
    LinkedIn: \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9} \\
    \vspace{-10pt}
\end{center}

%-----------EDUCATION-----------%
\section*{Education}
    \textbf{University of Southern California (USC)}, Los Angeles, CA \hfill Aug 2024 -- May 2026 \\
    \textit{Master of Science in Computer Engineering} \hfill GPA: 3.7/4.00 \\
    Relevant Coursework: Database Management Systems, AI Agents, Algorithms, Computer Networks. \\

    \vspace{2pt}
    \textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill April 2018 -- May 2022 \\
    \textit{B.Tech. in Electronics and Communication} \hfill CGPA: 9.04 / 10.00 \\
    Relevant Coursework: IoT Systems, Cloud Computing, Object Oriented Programming, Web Technologies.

%-----------SKILLS-----------%
\section*{Technical Skills}
    \textbf{Languages:} Python, SQL, Java, dbt, C++, JavaScript, HTML5, CSS3, APEX \\
    \textbf{Cloud \& DevOps:} AWS (CodePipeline, CodeBuild, Stacks), Airflow, Snowflake, CI/CD, Salesforce, MuleSoft, Git, Docker \\
    \textbf{Concepts:} Data Structures \& Algorithms, SDLC, RESTful APIs, Agile, Data Quality, ETL Pipelines, System Architecture \\
    \textbf{Tools \& Platforms:} Tableau, Postman, MQTT, Wireshark, Splunk, Datadog

%-----------EXPERIENCE-----------%
\section*{Work Experience}
    \textbf{Accenture}, Bangalore, India \hfill July 2022 -- Aug 2024 \\
    \textit{Advanced Application Developer}
    \begin{itemize}[leftmargin=*]
        \item Supervised transition from manual deployments to CI/CD pipeline, reducing turnaround time by 50\% and streamlining Dev-QA handoffs.
        \item Developed and maintained custom CRM applications using Salesforce and APEX; delivered 30+ API services using MuleSoft.
        \item Created resuable frameworks for logging and error handling prevented downtime and improved system reliability.
        \item Worked closely on various auth token caching and API rate limiting strategies.
    \end{itemize}

    \vspace{2pt}
    \textbf{University of Southern California}, Los Angeles, CA \hfill Jan 2025 -- Present \\
    \textit{Data Analyst, MANN School of Pharmacy} \hfill (May 2025 -- Present)
    \begin{itemize}[leftmargin=*]
        \item Helped build and test custom CRM applications on Salesforce and created data visualizations on Tableau.
    \end{itemize}
    
    \textit{Course Producer, EE354 (Intro to Digital Circuits)} \hfill (Aug 2025 -- Jan 2026)
    \begin{itemize}[leftmargin=*]
        \item Held office hours, graded assignments/exams, and managed logistics for Professor Gandhi.
    \end{itemize}
    
    \textit{Teaching Assistant, EE 457 (Computer Systems Organization)} \hfill (Jan 2025 -- Jan 2026)
    \begin{itemize}[leftmargin=*]
        \item Assisted Professor Puvvada in revamping assignments and developing strategies to improve student learning outcomes.
    \end{itemize}


%-----------RESEARCH-----------%
\section*{Research}
    \textbf{Learning Optimal Gateway Placement for Low-cost Smart Cities} \hfill USC, 2025
    \begin{itemize}[leftmargin=*]
        \item Enhanced placement methodologies and created simulations to realistically model real-world scenarios.
        \item Presented poster at 14th Annual Electrical Engineering Research Festival, USC.
    \end{itemize}
    
    \textbf{OpenCV-Based AI-Driven Customer Screening System} \hfill Springer Journal, 2024
    \begin{itemize}[leftmargin=*]
        \item Developed an AI-vision powered system for crowd management using OpenCV \& Machine Learning.
        \item Published findings in \textit{Wireless Personal Communications}, DOI: 10.1007/s11277-024-11286-x.
    \end{itemize}
%-----------PROJECTS-----------%
\section*{Projects}
    \textbf{Web Scrapers and Automation Suite} \hfill Selenium, Python, Automation
    \begin{itemize}[leftmargin=*]
        \item Implemented Selenium-based test suites to verify feature deployment consistency across multiple user profiles.
    \end{itemize}

    \textbf{Automated Google Form Submission Bot} \hfill Python (Flask), Scripting
    \begin{itemize}[leftmargin=*]
        \item Designed an automation bot using Python (Flask) to bulk-fill Google Forms, optimizing time by 98\% compared to manual entry.
    \end{itemize}

    \textbf{TCP/IP Socket Programming} \hfill Python, Computer Networks
    \begin{itemize}[leftmargin=*]
        \item Designed and implemented client-server systems for data packet exchange using Python TCP/IP sockets.
    \end{itemize}

    \textbf{IoT-Based Keyless Bike Access System} \hfill ESP8266, WiFi, Mobile App
    \begin{itemize}[leftmargin=*]
        \item Developed a keyless authentication system using ESP8266 and WiFi for bike access via a mobile app, facilitating secure vehicle sharing.
    \end{itemize}

%-----------CERTIFICATIONS & AWARDS-----------%
\section*{Certifications \& Awards}
    \begin{itemize}[leftmargin=*] \itemsep 0pt
        \item \textbf{MuleSoft Certified Developer (MCD - Level 1)} -- Certified 2023
        \item \textbf{Pinnacle TCI Award (Accenture):} Recognized for exceptional performance (Aug 2023).
        \item \textbf{Growth Catalyst Award (Accenture):} Awarded for outstanding contributions in growth initiatives (June 2023).
    \end{itemize}

\end{document}
