\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome5}


\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}


% Custom font
\usepackage{mathptmx}


% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{1in}

\titleformat{\section}{
  \vspace{-12pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule\vspace{-6pt}]

%Items formatting
\setlist[itemize]{
    leftmargin=2.5em,
    itemsep=0pt,
    topsep=0pt,        % removes space above list
    partopsep=0pt,     % removes extra paragraph spacing
    parsep=0pt         % removes spacing inside items
}

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}}\\
    {\normalsize Software Engineer \textbar\ Embedded Systems \& Controls}\\
    \small
    \faEnvelope\ \href{mailto:jaishah.work@gmail.com}{jaishah.work@gmail.com}
    \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9}
\end{center}
\vspace{-13pt}


%-----------EDUCATION-----------%
\section*{Education}
\textbf{University of Southern California}, \textit{Los Angeles, CA} \hfill Aug 2024 -- May 2026 \\
\textit{M.S. Computer Engineering} \hfill GPA: 3.7/4.0 \\
Relevant Coursework: Computer Architecture, Distributed Systems, Software Engineering, Database Management Systems

\textbf{Vellore Institute of Technology}, \textit{Vellore, India }\hfill Apr 2018 -- May 2022 \\
\textit{B.Tech. Electronics \& Communication (IoT \& Sensors)} \hfill CGPA: 9.04/10 \\
Relevant Coursework: IoT Systems, Signal Analysis, Advanced Microcontrollers, Object Oriented Programming


%-----------SKILLS-----------%
\section*{Technical Skills}
\textbf{Languages:} C/C++, Python, Embedded C, Verilog, Assembly, Java \\
\textbf{Embedded \& Architecture:} Microcontrollers (NodeMCU, ESP8266, Raspberry Pi), IoT, Sensors, FPGA Design, Real-time Systems, Hardware Abstractions, RTL Digital Design, Computer Architecture, Memory Coherence \\
\textbf{Tools \& OS:} Linux, Embedded Operating Systems, Git/Version Control, JIRA, ModelSim \\
\textbf{Software Practices:} Agile Scrum methodologies, Automated Test Tools, CI/CD pipelines, System Validation, OOP


%-----------EXPERIENCE-----------%
\section*{Professional Experience}
\textbf{Teaching Assistant – Digital Circuits \& Computer Systems Architecture} -- \textit{USC} \hfill Jan 2025 -- Dec 2025
\begin{itemize}
\item Mentored students in \textbf{RTL digital design, simulation, and hardware verification} using \textbf{Verilog} and \textbf{ModelSim}, providing hands-on instruction for embedded and microarchitectural testing.
\item Assisted with debugging and validating digital logic implementations on \textbf{hardware} and \textbf{simulation} environments, reinforcing best practices for systematic fault isolation and edge-case testing.
\item Explained complex hardware abstraction concepts including \textbf{pipelining}, \textbf{hazards}, and \textbf{memory hierarchy}.
\end{itemize}

\textbf{Research Assistant – Network Reconnaissance Lab} -- \textit{USC} \hfill Aug 2025 -- Dec 2025
\begin{itemize}
\item Modeled \textbf{networked embedded systems} to evaluate gateway placement \textbf{strategies minimizing latency} and infrastructure cost under the guidance of \textbf{Dr. C. Baker}.
\item Conducted simulation-driven architectural studies focusing on real-time data flow and controller communications, presenting findings at \textbf{USC’s Electrical Engineering Research Festival}.
\end{itemize}

\textbf{Software Engineer / Advanced Application Engineer} -- \textit{Accenture} \hfill July 2022 -- Aug 2024
\begin{itemize}
\item Designed and deployed automated \textbf{CI/CD pipelines} using \textbf{GitHub Actions} and \textbf{AWS CodePipeline}, actively testing and demonstrating software functionality readiness and reducing release turnaround time by \textbf{70\%}.
\item Authored \textbf{Python} scripts to automate internal deployment toolchains and improve operational troubleshooting.
\item Functioned as an inclusive \textbf{Agile Scrum} team member to deliver integrated software solutions, applying structured development, testing, and system-level debugging workflows.
\end{itemize}


%-----------PROJECTS-----------%
\section*{Projects}
\textbf{Smart Mirror IoT Automation Platform} \hfill 2020--2021
\begin{itemize}
\item Architected a distributed IoT system using \textbf{MQTT publish–subscribe messaging} to coordinate communication between edge devices (\textbf{Raspberry Pi} and \textbf{ESP8266}) and a central controller.
\item Implemented real-time communication between embedded sensor nodes and user interface displays, designing event-driven automation workflows with \textbf{Python} services.
\item Delivered common infrastructure solutions for telemetry ingestion and device orchestration across a local network.
\end{itemize}

\textbf{IoT-Based Keyless Bike Access System} \hfill 2019
\begin{itemize}
\item Designed dual-mode wireless authentication using \textbf{NodeMCU} with \textbf{Bluetooth/WiFi} communication for secure embedded automotive access logic.
\item Engineered a resilient, locally hosted embedded server supporting real-time diagnostics and redundant connectivity.
\end{itemize}

\textbf{RISC-V Processor Design using RTL} \hfill 2024
\begin{itemize}
\item Designed a \textbf{5-stage pipelined processor} integrating \textbf{forwarding} and hazard detection control logic to resolve pipeline dependencies.
\item Verified and demonstrated software functionality and component readiness through intense simulation testbenches utilizing continuous automated validation techniques.
\end{itemize}

\textbf{Alarm Clock on FPGA} \hfill 2019
\begin{itemize}
\item Developed a synthesizable \textbf{Verilog} system deployed on \textbf{FPGA} hardware with modular timing and display control.
\item Designed multiplexed \textbf{7-segment} driver logic and validated timing edge cases.
\end{itemize}

\end{document}
