\documentclass[letterpaper,10pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Custom font
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

%Items formatting
\setlist[itemize]{topsep=1.5pt}
% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}} \\
    \vspace{2pt}
    \small
    Ph: +1 (323) 334-7408 \quad Email: \href{mailto:jaijayes@usc.edu}{jaijayes@usc.edu} \\
    LinkedIn: \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9} \\
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------%
\section*{Education}
\textbf{University of Southern California (USC)}, Los Angeles, CA \hfill Aug 2024 -- May 2026 \\
\textit{Master of Science in Computer Engineering} \hfill GPA: 3.7/4.00 \\
Relevant Coursework: Computer Networks, Algorithms, Database Management Systems, AI Agents. \\
\vspace{2pt}
\textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill April 2018 -- May 2022 \\
\textit{B.Tech. in Electronics and Communication} \hfill CGPA: 9.04/10.00 \\
Relevant Coursework: Object Oriented Programming, web Technologies, Cloud Computing.

%-----------SKILLS-----------%
\section*{Technical Skills}
\textbf{Languages:} Python, Java, SQL, C++, JavaScript, HTML5, CSS3, Verilog. \\
\textbf{Cloud \& DevOps:} AWS (CodePipeline, CodeBuild), CI/CD pipelines, Docker, Splunk, Datadog. \\
\textbf{Frameworks \& Tools:} Flask, MuleSoft, Git, GitHub Actions, JIRA, Node-RED, MQTT. \\
\textbf{Concepts:} RESTful APIs, SDLC, Agile, Scrum, Kanban, Data Structures, Web Scraping.

%-----------EXPERIENCE-----------%
\section*{Work Experience}
\textbf{Accenture}, Bangalore, India \hfill July 2022 -- Aug 2024 \\
\textit{Advanced Application Developer}
\begin{itemize}
    \item Supervised transition from manual deployments to CI/CD pipeline, reducing turnaround time by 50\% and streamlining Dev-QA handoffs.
    \item Created reusable frameworks for logging and error handling for the company, significantly improving system observability.
    \item Developed and maintained custom CRM applications, delivering 30+ API services using MuleSoft.
    \item Collaborated with Quality Assurance teams to ensure defect-free software and appropriate test case development.
    \item Worked in an Agile environment (Scrum), participating in sprint planning and retrospectives to enable progress.
\end{itemize}

\textbf{University of Southern California}, Los Angeles, CA \hfill May 2025 -- Present \\
\textit{Data Analyst, MANN School of Pharmacy}
\begin{itemize}
    \item Helping build and test custom CRM applications on Salesforce, ensuring data integrity and effective user interfaces.
    \item Utilizing Tableau for data visualization, translating technical data into actionable insights for non-technical stakeholders.
\end{itemize}

\textbf{University of Southern California}, Los Angeles, CA \hfill Jan 2025 -- Jan 2026 \\
\textit{Teaching Assistant, EE 457 / Course Producer, EE 354}
\begin{itemize}
    \item Assisted professors in revamping assignments and developing strategies to improve student learning outcomes.
    \item Demonstrated leadership by managing logistics and effectively communicating complex technical concepts to students.
\end{itemize}

%-----------PROJECTS-----------%
\section*{Projects}
\textbf{Web Scrapers and Automation Suite} \hfill Python, Selenium \\
\begin{itemize}
    \item Implemented Selenium-based test suites to verify feature deployment consistency across multiple user profiles.
    \item Developed automation scripts to reduce manual effort in routine data extraction tasks, ensuring high data accuracy.
\end{itemize}

\textbf{Automated Google Form Submission Bot} \hfill Python, Flask \\
\begin{itemize}
    \item Designed an automation bot using Python (Flask) to bulk-fill Google Forms, optimizing time by 98\% compared to manual entry.
    \item Integrated robust error handling to trace defects and manage technical debt effectively.
\end{itemize}

\textbf{TCP/IP Socket Programming} \hfill Python, Networking \\
\begin{itemize}
    \item Designed and implemented client-server systems for data packet exchange using Python TCP/IP sockets.
    \item Focused on reliable data transfer and network protocol implementation.
\end{itemize}



%-----------CERTIFICATIONS & AWARDS-----------%
\section*{Certifications \& Awards}
\begin{itemize} \itemsep -2pt
    \item \textbf{MuleSoft Certified Developer (MCD - Level 1)} -- Certified 2023.
    \item \textbf{Pinnacle TCI Award (Accenture):} Recognized for exceptional performance (Aug 2023).
    \item \textbf{Growth Catalyst Award (Accenture):} Awarded for outstanding contributions in growth initiatives (June 2023).
\end{itemize}

\end{document}
