\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome5}


\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}


% Custom font
\usepackage{mathptmx}


% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{1in}

\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule\vspace{-6pt}]

%Items formatting
\setlist[itemize]{
    leftmargin=2.5em,
    itemsep=2pt,
    topsep=0pt,        % removes space above list
    partopsep=0pt,     % removes extra paragraph spacing
    parsep=0pt         % removes spacing inside items
}

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}}\\
    {\normalsize Healthcare Data Analyst \textbar\ BI Analytics \& Reporting}\\
    \small
    \faEnvelope\ \href{mailto:jaishah.work@gmail.com}{jaishah.work@gmail.com}
    \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9}
\end{center}
\vspace{-13pt}


%-----------EDUCATION-----------%
\section*{Education}
\textbf{University of Southern California}, \textit{Los Angeles, CA} \hfill Aug 2024 -- May 2026 \\
M.S. Computer Engineering \hfill GPA: 3.7/4.0 \\
Relevant Coursework: Database Management Systems, Distributed Systems, Algorithms, Computer Networks

\vspace{4pt}

\textbf{Vellore Institute of Technology}, \textit{Vellore, India }\hfill Apr 2018 -- May 2022 \\
B.Tech. Electronics \& Communication (IoT \& Sensors) \hfill CGPA: 9.04/10


%-----------SKILLS-----------%
\section*{Technical Skills}
\textbf{Data \& Analytics:} SQL, Tableau, ETL Pipelines, Data Visualization, Data Cleaning, Data Validation, Predictive Analytics, Data Mining, HIPAA Compliance \\
\textbf{Cloud \& Platforms:} AWS, GitHub Actions, Docker, Splunk, Datadog \\
\textbf{Integration \& Databases:} Postman, PostgreSQL, REST APIs \\
\textbf{Programming:} Python, Java, C++, JavaScript \\
\textbf{Tools \& Frameworks:} CareKit, Flask, OpenCV, JIRA


%-----------EXPERIENCE-----------%
\section*{Professional Experience}
\textbf{Data Analyst} -- \textit{USC MANN School of Pharmacy} \hfill May 2025 -- Present
\begin{itemize}
\item Developed \textbf{Tableau + SQL analytics solutions} to transform large-scale datasets into actionable insights, deploying dashboards to on-premise \textbf{Tableau Server} for organization-wide access.
\item Engineered \textbf{data processing and ETL-style workflows} including cleaning, transformation, and relational joins to support accurate reporting pipelines.
\item Enhanced \textbf{Salesforce data models} across \textbf{70+ objects} and delivered \textbf{30+ analytical reports} used by \textbf{50+ stakeholders}.
\item Automated validation and testing using \textbf{Python} and LLM-driven scripts, processing \textbf{100,000+ records} and reducing manual reporting by \textbf{15 hours/week}.
\end{itemize}

\textbf{Advanced Application Engineer} -- \textit{Accenture} \hfill July 2022 -- Aug 2024
\begin{itemize}
\item Designed and deployed automated \textbf{CI/CD pipelines} using \textbf{GitHub Actions} and \textbf{AWS CodePipeline}, reducing release turnaround time by \textbf{70\%} and enabling reliable continuous delivery.
\item Built and scaled \textbf{30+ RESTful microservices and APIs} supporting backend system design for \textbf{10k+ daily transactions}, improving distributed system integration, scalability, and production reliability.
\item Authored OpenAPI specifications and implemented centralized error-handling frameworks, reducing debugging time by 40\%.
\item Integrated monitoring using Splunk and Datadog to ensure data reliability and operational visibility.
\end{itemize}


%-----------PROJECTS-----------%
\section*{Projects}
\textbf{Healthcare \& Behavioral Insights App} \hfill 2026
\begin{itemize}
\item Designed a longitudinal health-data analytics platform using \textbf{CareKit} to collect, store, and analyze patient-reported outcomes.
\item Built structured data pipelines with \textbf{PostgreSQL} to manage secure ingestion, transformation, and retrieval of health metrics.
\item Developed visualization workflows to identify trends and behavioral insights, increasing user engagement by \textbf{25\%}.
\end{itemize}

\textbf{AadharVision Real-time Data Platform} \hfill 2021
\begin{itemize}
\item Developed a real-time data aggregation system to track occupancy and compliance metrics using computer vision inputs.
\item Built backend workflows to process OCR-derived identity data and integrate validated records into reporting pipelines.
\item Enabled analytics-driven alerts and monitoring dashboards to support operational decision-making.
\end{itemize}

\textbf{Smart Mirror IoT Analytics Platform} \hfill 2020--2021
\begin{itemize}
\item Engineered a real-time data streaming pipeline using MQTT to collect environmental and device telemetry.
\item Designed Node-RED workflows to transform, route, and visualize incoming data for live monitoring dashboards.
\item Built event-driven automation enabling continuous updates and analytics-based notifications.
\end{itemize}


%-----------CERTIFICATIONS & AWARDS-----------%
\section*{Certifications}
MuleSoft Certified Developer (MCD Level 1)

\end{document}
