\documentclass[letterpaper,10pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Custom font
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

%Items formatting
\setlist[itemize]{topsep=1.5pt}
% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}} \\
    \vspace{2pt}
    \small
    Ph: +1 (323) 334-7408 \quad Email: \href{mailto:jaijayes@usc.edu}{jaijayes@usc.edu} \\
    LinkedIn: \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9} \\
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------%
\section*{Education}
\textbf{University of Southern California (USC)}, Los Angeles, CA \hfill Aug 2024 -- May 2026 \\
\textit{Master of Science in Computer Engineering} \hfill GPA: 3.7/4.00 \\
Relevant Coursework: Algorithms, Computer Networks (TCP/IP), Computer Architecture, Database Management Systems. \\
\vspace{2pt}
\textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill April 2018 -- May 2022 \\
\textit{B.Tech. in Electronics and Communication} \hfill CGPA: 9.04/10.00 \\
Relevant Coursework: Object Oriented Programming, Web Technologies, Cloud Computing, IoT Systems.

%-----------SKILLS-----------%
\section*{Technical Skills}
\textbf{Languages:} Java, C++, Python, SQL, C, JavaScript, Verilog, Assembly, HTML5, CSS3. \\
\textbf{Tools \& Platforms:} Git, GitHub, JIRA, VS Code, Linux, AWS, Docker, Salesforce, MuleSoft. \\
\textbf{Methodologies \& Concepts:} Agile/Scrum, CI/CD Pipelines, RESTful APIs, TCP/IP, SDLC, Debugging. \\
\textbf{Web \& Data:} Node.js, React (Basics), Flask, JSON, DOM, NoSQL, Relational Databases.

%-----------EXPERIENCE-----------%
\section*{Work Experience}
\textbf{Accenture}, Bangalore, India \hfill July 2022 -- Aug 2024 \\
\textit{Advanced Application Developer}
\begin{itemize}
    \item Collaborated in an Agile environment to deliver high-quality enterprise software solutions.
    \item Supervised transition from manual deployments to CI/CD pipeline, reducing turnaround time by 50\% and streamlining Dev-QA handoffs.
    \item Developed and maintained custom CRM applications, delivering 30+ API services using MuleSoft and Salesforce.
    \item Applied analytical and debugging skills to resolve defects and manage technical debt effectively.
    \item Created reusable frameworks for logging and error handling, improving system reliability and maintainability.
\end{itemize}

\textbf{University of Southern California}, Los Angeles, CA \hfill May 2025 -- Present \\
\textit{Data Analyst, MANN School of Pharmacy}
\begin{itemize}
    \item Helping build and test custom CRM applications on Salesforce and created data visualizations on Tableau.
    \item Translating technical requirements into functional software solutions for business stakeholders.
\end{itemize}

\textbf{University of Southern California}, Los Angeles, CA \hfill Jan 2025 -- Jan 2026 \\
\textit{Teaching Assistant, EE 457 / Course Producer, EE 354}
\begin{itemize}
    \item Mentored students in computer organization and digital circuits, fostering a collaborative learning environment.
    \item Managed logistics and graded assignments, ensuring timely feedback and support for student success.
\end{itemize}

%-----------PROJECTS-----------%
\section*{Projects}
\textbf{TCP/IP Socket Programming} \hfill Python, Networking \\
\begin{itemize}
    \item Designed and implemented client-server systems for data packet exchange using Python TCP/IP sockets.
    \item demonstrated understanding of reliable data transfer, network protocols, and socket communication.
\end{itemize}

\textbf{Microarchitecture Design (EE 457 Course Project)} \hfill Verilog, Computer Architecture \\
\begin{itemize}
    \item Designed and simulated single-cycle CPUs, ALUs, and Tomasulo machines using Verilog.
    \item Implemented advanced concepts including out-of-order execution and hazard detection, relevant to system programming.
\end{itemize}

\textbf{Web Scrapers and Automation Suite} \hfill Python, Selenium \\
\begin{itemize}
    \item Implemented Selenium-based test suites to verify feature deployment consistency across multiple user profiles.
    \item developed tools to automate routine tasks, significantly reducing manual effort.
\end{itemize}



%-----------CERTIFICATIONS & AWARDS-----------%
\section*{Certifications \& Awards}
\begin{itemize} \itemsep -2pt
    \item \textbf{MuleSoft Certified Developer (MCD - Level 1)} -- Certified 2023.
    \item \textbf{Pinnacle TCI Award (Accenture):} Recognized for exceptional performance (Aug 2023).
    \item \textbf{Growth Catalyst Award (Accenture):} Awarded for outstanding contributions in growth initiatives.
\end{itemize}

\end{document}
