\documentclass[letterpaper,10pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Custom font
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

%Items formatting
\setlist[itemize]{topsep=0pt, itemsep=-2pt}
% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}} \\
    \vspace{2pt}
    \small
    Ph: +1 (323) 334-7408 \quad Email: \href{mailto:jaijayes@usc.edu}{jaijayes@usc.edu} \\
    LinkedIn: \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9} \\
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------%
\section*{Education}
\textbf{University of Southern California (USC)}, Los Angeles, CA \hfill Aug 2024 -- May 2026 \\
\textit{Master of Science in Computer Engineering} \hfill GPA: 3.7/4.00 \\
Relevant Coursework: \textbf{AI Agents}, Advanced Computer Architecture, Computer Systems Organization, Algorithms. \\
\vspace{2pt}
\textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill April 2018 -- May 2022 \\
\textit{B.Tech. in Electronics and Communication} \hfill CGPA: 9.04/10.00 \\
Relevant Coursework: IoT Systems, Microcontrollers, Object Oriented Programming.

%-----------SKILLS-----------%
\section*{Technical Skills}
\textbf{Agentic AI \& ML:} \textbf{Agentic AI}, LLMs, Ollama, Vibe Coding, Computer Vision, Machine Learning, OpenCV. \\
\textbf{Hardware \& Architecture:} Computer Architecture, FPGA Design, GPU Constraints, Verilog, Raspberry Pi, IoT. \\
\textbf{Languages \& Tools:} Python, C++, C, SQL, Git, Linux, VS Code, Docker. \\
\textbf{Concepts:} \textbf{Low-Cost Hardware Optimization}, Quantization, Model Deployment, SDLC, Automation.

%-----------EXPERIENCE-----------%
\section*{Work Experience}
\textbf{University of Southern California}, Los Angeles, CA \hfill Jan 2025 -- Jan 2026 \\
\textit{Teaching Assistant, EE 457 (Computer Systems Organization)}
\begin{itemize}
    \item Mentored students on instruction-level parallelism, pipelining, and hazard detection, directly relevant to hardware constraints.
    \item Assisted in designing assignments that require optimization of hardware resources (ALU, Memory).
    \item Communicated complex computer architecture concepts to a diverse group of students.
\end{itemize}

\textbf{Accenture}, Bangalore, India \hfill July 2022 -- Aug 2024 \\
\textit{Advanced Application Developer}
\begin{itemize}
    \item Supervised transition from manual deployments to CI/CD pipeline, optimizing system reliability and deployment times.
    \item Developed automation tools and error-handling frameworks, enhancing operational efficiency.
    \item Collaborated in an Agile environment to deliver robust software solutions.
\end{itemize}

\textbf{University of Southern California}, Los Angeles, CA \hfill May 2025 -- Present \\
\textit{Data Analyst, MANN School of Pharmacy}
\begin{itemize}
    \item Analyzed data workflows and implemented CRM solutions to improve data management efficiency.
\end{itemize}

%-----------PROJECTS-----------%
\section*{Projects}
\textbf{Microarchitecture Design (EE 457 Course Project)} \hfill Verilog, Computer Architecture \\
\begin{itemize}
    \item Designed and simulated single-cycle CPUs, ALUs, and Tomasulo machines using Verilog.
    \item Optimized hardware for out-of-order execution and hazard detection, demonstrating understanding of \textbf{hardware constraints}.
    \item Gained deep knowledge of how instructions interact with hardware, essential for low-cost AI optimization.
\end{itemize}

\textbf{OpenCV-Based AI-Driven Customer Screening System} \hfill Python, Computer Vision \\
\begin{itemize}
    \item Developed an AI-vision powered system for crowd management using OpenCV \& Machine Learning.
    \item Optimized the model to run efficiently on standard hardware for real-time processing.
\end{itemize}

\textbf{Automated Google Form Submission Bot} \hfill Python, Flask \\
\begin{itemize}
    \item Designed an automation bot to bulk-fill forms, acting as a prototype for agentic workflow automation.
    \item Implemented logic to handle errors and adapt to changing form inputs dynamically.
\end{itemize}



\textbf{Smart Mirror with MQTT Home Automation} \hfill IoT, Raspberry Pi \\
\begin{itemize}
    \item Built a Smart Mirror using Raspberry Pi and ESP8266, integrating local hardware with cloud services.
    \item Demonstrated ability to build and configure physical computer systems and manage hardware constraints.
\end{itemize}

%-----------RESEARCH-----------%
\section*{Research}
\textbf{Learning Optimal Gateway Placement for Low-cost Opportunistic Smart Cities} \\
\textit{Network Reconnaissance Lab, USC}
\begin{itemize}
    \item Enhanced placement methodologies to optimize network infrastructure costs.
    \item Analyzed trade-offs between performance and cost in simulated environments.
\end{itemize}

\end{document}
