\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome5}


\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}


% Custom font
\usepackage{mathptmx}


% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{1in}

\titleformat{\section}{
  \vspace{-12pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule\vspace{-6pt}]

%Items formatting
\setlist[itemize]{
    leftmargin=2.5em,
    itemsep=0pt,
    topsep=0pt,        % removes space above list
    partopsep=0pt,     % removes extra paragraph spacing
    parsep=0pt         % removes spacing inside items
}

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}}\\
    {\normalsize Software Engineer II \textbar\ Data Engineering \& ETL Pipelines}\\
    \small
    \faEnvelope\ \href{mailto:jaishah.work@gmail.com}{jaishah.work@gmail.com}
    \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9}
\end{center}
\vspace{-13pt}


%-----------EDUCATION-----------%
\section*{Education}
\textbf{University of Southern California}, \textit{Los Angeles, CA} \hfill Aug 2024 -- May 2026 \\
M.S. Computer Engineering \hfill GPA: 3.7/4.0 \\
Relevant Coursework: Database Management Systems, Distributed Systems, Software Engineering, Algorithms

\vspace{4pt}

\textbf{Vellore Institute of Technology}, \textit{Vellore, India }\hfill Apr 2018 -- May 2022 \\
B.Tech. Electronics \& Communication (IoT \& Sensors) \hfill CGPA: 9.04/10


%-----------SKILLS-----------%
\section*{Technical Skills}
\textbf{Data Engineering \& Pipelines:} SQL, Python, ETL Pipelines, Data Modeling, Data Processing, Data Transformation, Data Quality Monitoring, Automated Testing Frameworks, Tableau, Data Visualization \\
\textbf{Software Engineering Practices:} Object-Oriented Programming (OOP), CI/CD pipelines, GitHub Actions, System Architecture, Code Review, Operations Support, End-to-End Testing \\
\textbf{Cloud, DevOps \& Platforms:} AWS, Docker, PostgreSQL, Splunk, Datadog \\
\textbf{Programming \& Tools:} Python, Java, C++, JavaScript, Web Scraping, RESTful APIs, JIRA, Agile \\
\textbf{Machine Learning \& Data:} Feature Engineering, Model Evaluation Metrics, Data Collection Workflows


%-----------EXPERIENCE-----------%
\section*{Professional Experience}
\textbf{Data Analyst} -- \textit{USC MANN School of Pharmacy} \hfill May 2025 -- Present
\begin{itemize}
\item Developed \textbf{Tableau + SQL analytics solutions} to transform large-scale datasets into actionable insights, deploying dashboards to on-premise \textbf{Tableau Server} for organization-wide access.
\item Engineered \textbf{data processing and ETL-style workflows} including cleaning, transformation, and relational joins to support accurate SQL reporting pipelines.
\item Automated validation and testing using \textbf{Python} and LLM-driven scripts, processing \textbf{100,000+ records} and effectively reducing manual data entry and reporting by \textbf{15 hours/week}.
\item Enhanced \textbf{Salesforce data models} across \textbf{70+ objects} and delivered \textbf{30+ analytical reports} used by \textbf{50+ stakeholders}.
\end{itemize}

\textbf{Advanced Application Engineer} -- \textit{Accenture} \hfill July 2022 -- Aug 2024
\begin{itemize}
\item Built scalable data integration and transformation workflows enabling CRM analytics and system synchronization.
\item Designed and deployed automated \textbf{CI/CD pipelines} using \textbf{GitHub Actions} and \textbf{AWS CodePipeline}, reducing release turnaround time by \textbf{70\%} and enabling reliable continuous delivery.
\item Built and scaled 30+ RESTful microservices and APIs supporting backend system design for 10k+ daily transactions, improving distributed system integration, scalability, and production reliability.
\item Integrated monitoring and data logging pipelines using Splunk and Datadog to ensure data reliability, troubleshooting mechanisms, and operational capability.
\end{itemize}


%-----------PROJECTS-----------%
\section*{Projects}
\textbf{Healthcare \& Behavioral Insights App} \hfill 2026
\begin{itemize}
\item Built containerized backend services with \textbf{Docker} and \textbf{PostgreSQL}, deploying to \textbf{Heroku} to enable scalable data persistence and secure health record management.
\item Designed a longitudinal health-data analytics platform using CareKit to collect, store, and analyze patient-reported outcomes.
\item Built structured data pipelines with PostgreSQL to manage secure ingestion, transformation, and retrieval of health metrics.
\end{itemize}

\textbf{AadharVision Real-time Data Platform} \hfill 2021
\begin{itemize}
\item Developed a real-time data aggregation system to track occupancy and compliance metrics using computer vision inputs.
\item Built backend workflows to process OCR-derived identity data and integrate validated records into reporting pipelines.
\item Enabled analytics-driven alerts and monitoring dashboards to support operational decision-making.
\end{itemize}

\textbf{Web Scrapers and Automation Suite} \hfill 2018--Present
\begin{itemize}
\item Implemented \textbf{Selenium-based} test suites to verify feature deployment consistency across multiple user profiles.
\item Implemented web scrapers to extract data for backup from outdated legacy systems.
\end{itemize}


%-----------CERTIFICATIONS & AWARDS-----------%
\section*{Certifications}
MuleSoft Certified Developer (MCD Level 1)

\end{document}
