\documentclass[letterpaper,10pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Custom font
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

%Items formatting
\setlist[itemize]{topsep=1pt}
% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}} \\
    \vspace{5pt}
    \small
    Ph: +1 (323) 334-7408 \quad Email: \href{mailto:jaijayes@usc.edu}{jaijayes@usc.edu} \\
    LinkedIn: \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9} \\
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------%
\section*{Education}
\textbf{University of Southern California (USC)}, Los Angeles, CA \hfill Aug 2024 -- May 2026 \\
\textit{Master of Science in Computer Engineering} \hfill GPA: 3.6/4.00 \\
Related Coursework: AI Agents, Database Management Systems, Algorithms, Computer Networks.

\vspace{2pt}

\textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill April 2018 -- May 2022 \\
\textit{B.Tech. in Electronics and Communication (IoT and Sensors)} \hfill CGPA: 9.04 / 10.00 \\
Related Coursework: IoT Systems, Cloud Computing, Object Oriented Programming, Web Technologies.

%-----------SKILLS-----------%
\section*{Technical Skills}
\textbf{Languages:} Python, Java, SQL, MySQL, APEX, JavaScript, HTML5, CSS3, PHP \\
\textbf{Automation \& DevOps:} GitHub, JIRA, CI/CD Pipelines, AWS (CodePipeline, CodeBuild), Selenium, Flask \\
\textbf{SaaS \& Integration:} Salesforce CRM, Salesforce Admin, MuleSoft, Tableau, RESTful APIs, JSON \\
\textbf{AI \& Tools:} AI Agents, ChatGPT, Vibe Coding, OpenCV, VS Code, Linux, Postman

%-----------EXPERIENCE-----------%
\section*{Work Experience}
\textbf{Accenture}, Bangalore, India \hfill July 2022 -- Aug 2024 \\
\textit{Backend Developer}
\begin{itemize}
    \item Spearheaded transition from manual deployments to CI/CD pipeline, reducing turnaround time by 50\% and streamlining Dev-QA handoffs.
    \item Developed and maintained custom CRM applications using Salesforce and APEX; delivered 30+ API services using MuleSoft.
    \item Optimized deployment processes and collaborated with cross-functional teams to enhance system reliability.
    \item Recognized for exceptional performance with the Pinnacle TCI Award and Growth Catalyst Award.
\end{itemize}

\textbf{MANN School of Pharmacy (USC)}, Los Angeles, CA \hfill May 2025 -- Present \\
\textit{Data Analyst}
\begin{itemize}
    \item Helped build and test custom CRM applications on Salesforce and created data visualizations on Tableau.
    \item Analyzed data requirements to support business operations and improve decision-making processes.
\end{itemize}

\textbf{University of Southern California}, Los Angeles, CA \hfill Jan 2025 -- Jan 2026 \\
\textit{Teaching Assistant, EE 457 (Computer Systems Organization)}
\begin{itemize}
    \item Assisted Professor Puvvada in revamping assignments and developing strategies to improve student learning outcomes.
    \item Held office hours, graded assignments/exams, and managed logistics for the course.
\end{itemize}

%-----------PROJECTS-----------%
\section*{Projects}
\textbf{Automated Google Form Submission Bot} \hfill Python, Flask
\begin{itemize}
    \item Designed an automation bot using Python (Flask) to bulk-fill Google Forms, optimizing time by 98\% compared to manual entry.
    \item Streamlined data entry processes for high-volume operations.
\end{itemize}

\textbf{Web Scrapers and Automation Suite} \hfill Python, Selenium
\begin{itemize}
    \item Implemented Selenium-based test suites to verify feature deployment consistency across multiple user profiles.
    \item Developed scripts to automate data collection and validation tasks.
\end{itemize}

\textbf{IoT-Based Keyless Bike Access System} \hfill ESP8266, WiFi, Mobile App
\begin{itemize}
    \item Developed a keyless authentication system using ESP8266 and WiFi for bike access via a mobile app, facilitating secure vehicle sharing.
\end{itemize}

\textbf{Smart Mirror with MQTT Home Automation} \hfill Raspberry Pi, MQTT
\begin{itemize}
    \item Built a Smart Mirror using Raspberry Pi and ESP8266, integrated with home automation via MQTT to control appliances and display real-time info.
\end{itemize}

%-----------CERTIFICATIONS & AWARDS-----------%
\section*{Certifications \& Awards}
\begin{itemize} \itemsep -2pt
    \item \textbf{Awards:} Pinnacle TCI Award, Growth Catalyst Award (Accenture).
    \item \textbf{Certifications:} MuleSoft Certified Developer.
    \item \textbf{Workshops:} Future of Computer Architecture and Hardware Security, Tableau Next.
\end{itemize}

\end{document}
