\documentclass[letterpaper,10pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Custom font
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-15pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

%Items formatting
\setlist[itemize]{topsep=0pt, itemsep=1pt}
% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}} \\
    \vspace{2pt}
    \small
    Ph: +1 (323) 334-7408 \quad Email: \href{mailto:jaijayes@usc.edu}{jaijayes@usc.edu} \\
    LinkedIn: \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9} \\
    \vspace{-15pt}
\end{center}

%-----------EDUCATION-----------%
\section*{Education}
    \textbf{University of Southern California (USC)}, Los Angeles, CA \hfill Aug 2024 -- May 2026 \\
    \textit{Master of Science in Computer Engineering} \hfill GPA: 3.7/4.00 \\
    Relevant Coursework: Algorithms, Database Management Systems, Computer Networks, AI Agents, Computer Architecture. \\

    \vspace{2pt}
    \textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill April 2018 -- May 2022 \\
    \textit{B.Tech. in Electronics and Communication} \hfill CGPA: 9.04 / 10.00 \\
    Relevant Coursework: Cloud Computing, Object Oriented Programming, Web Technologies, IoT Systems.

%-----------SKILLS-----------%
\section*{Technical Skills}
    \textbf{Languages:} Python, Java, C++, SQL, JavaScript, HTML5, CSS3, Verilog, C, APEX, DataWeave \\
    \textbf{Cloud \& DevOps:} AWS (CodePipeline, CodeBuild, Stacks), CI/CD, GitHub Actions, JIRA, Linux \\
    \textbf{Frameworks \& Tools:} Flask, Bootstrap, RESTful APIs, MuleSoft, Salesforce, Postman, MQTT, Pandas, NumPy \\
    \textbf{Concepts:} Data Structures \& Algorithms, SDLC, Agile, Scrum, API Design, Web Scraping, AI Agents

%-----------EXPERIENCE-----------%
\section*{Work Experience}
    \textbf{Accenture}, Bangalore, India \hfill July 2022 -- Aug 2024 \\
    \textit{Advanced Application Developer}
    \begin{itemize}[leftmargin=*]
        \item Supervised transition from manual deployments to CI/CD pipeline, reducing turnaround time by 50\% and streamlining Dev-QA handoffs.
        \item Developed and maintained custom CRM applications using Salesforce and APEX; delivered 30+ API services using MuleSoft.
        \item Created reusable frameworks for logging and error handling for the company, improving system reliability.
        \item Worked closely on various auth token caching and API rate limiting strategies for scale.
    \end{itemize}

    \textbf{University of Southern California}, Los Angeles, CA \hfill May 2025 -- Present \\
    \textit{Data Analyst, MANN School of Pharmacy}
    \begin{itemize}[leftmargin=*]
        \item Helped build and test custom CRM applications on Salesforce and created data visualizations on Tableau.
    \end{itemize}

    \textbf{University of Southern California}, Los Angeles, CA \hfill Aug 2025 -- Jan 2026 \\
    \textit{Course Producer, EE354 (Intro to Digital Circuits)}
    \begin{itemize}[leftmargin=*]
        \item Held office hours, graded assignments/exams, and managed logistics for Professor Gandhi.
    \end{itemize}

%-----------RESEARCH-----------%
\section*{Research}
    \textbf{OpenCV-Based AI-Driven Customer Screening System} \hfill Springer Journal, 2024
    \begin{itemize}[leftmargin=*]
        \item Developed an AI-vision powered system for crowd management using OpenCV \& Machine Learning.
        \item Published findings in \textit{Wireless Personal Communications}, DOI: 10.1007/s11277-024-11286-x.
    \end{itemize}
    
    \vspace{-2pt}
    \textbf{Learning Optimal Gateway Placement for Low-cost Smart Cities} \hfill USC, 2025
    \begin{itemize}[leftmargin=*]
        \item Enhanced placement methodologies and created simulations to realistically model real-world scenarios.
        \item Presented poster at 14th Annual Electrical Engineering Research Festival, USC.
    \end{itemize}

%-----------PROJECTS-----------%
\section*{Projects}
    \textbf{Automated Google Form Submission Bot} \hfill Python, Flask, Automation
    \begin{itemize}[leftmargin=*]
        \item Designed an automation bot using Python (Flask) to bulk-fill Google Forms, optimizing time by 98\% compared to manual entry.
        \item Engineered robust error handling to ensure data integrity during high-volume submissions.
    \end{itemize}

    \vspace{-2pt}
    \textbf{Web Scrapers and Automation Suite} \hfill Selenium, Python, Testing
    \begin{itemize}[leftmargin=*]
        \item Implemented Selenium-based test suites to verify feature deployment consistency across multiple user profiles.
        \item Automated repetitive data collection tasks, significantly reducing manual effort.
    \end{itemize}

    \vspace{-2pt}
    \textbf{Smart Mirror with MQTT Home Automation} \hfill IoT, Raspberry Pi, MQTT
    \begin{itemize}[leftmargin=*]
        \item Built a Smart Mirror using Raspberry Pi and ESP8266, integrated with home automation via MQTT.
        \item Enabled control of appliances and display of real-time information through a unified interface.
    \end{itemize}

    \vspace{-2pt}
    \textbf{Microarchitecture Design (EE 457)} \hfill Verilog, Computer Architecture
    \begin{itemize}[leftmargin=*]
        \item Designed and simulated single-cycle CPUs, ALUs, and Tomasulo machines using Verilog and Questasim.
        \item Implemented advanced concepts including register renaming, hazard detection, and out-of-order execution.
    \end{itemize}

%-----------CERTIFICATIONS & AWARDS-----------%
\section*{Certifications \& Awards}
    \begin{itemize}[leftmargin=*] \itemsep -2pt
        \item \textbf{MuleSoft Certified Developer (MCD - Level 1)} -- Certified 2023
        \item \textbf{Pinnacle TCI Award (Accenture):} Recognized for exceptional performance (Aug 2023).
        \item \textbf{Growth Catalyst Award (Accenture):} Awarded for outstanding contributions in growth initiatives (June 2023).
        \item \textbf{National Cyber Olympiad (SOF):} Achieved Zonal Rank 1 in 2015 \& 2016.
    \end{itemize}

\end{document}
