\documentclass[letterpaper,10pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Custom font
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-7pt}]

%Items formatting
\setlist[itemize]{topsep=0pt}
% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}} \\
    \vspace{2pt}
    \small
    Ph: +1 (323) 334-7408 \quad Email: \href{mailto:jaijayes@usc.edu}{jaijayes@usc.edu} \\
    LinkedIn: \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9} \quad Availability: May 2026 \\
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------%
\section*{Education}
\textbf{University of Southern California (USC)}, Los Angeles, CA \hfill Aug 2024 -- May 2026 \\
\textit{Master of Science in Computer Engineering} \hfill GPA: 3.7/4.00 \\
Relevant Coursework: Computer System Architecture (EE-457), Advanced Computer Architecture (EE-557), Computer Networks (EE-450), Algorithms (CSCI-570), Database Management Systems.

\vspace{1pt}

\textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill April 2018 -- May 2022 \\
\textit{B.Tech. in Electronics and Communication (IoT and Sensors)} \hfill CGPA: 9.04 / 10.00 \\
Relevant Coursework: IoT Systems, Advanced Microcontrollers, Signal Analysis, Object Oriented Programming.

%-----------SKILLS-----------%
\section*{Technical Skills}
\textbf{Languages:} C, C++, CUDA, Verilog, Python, SystemVerilog, Assembly, Java, SQL, Embedded C \\
\textbf{Hardware \& Tools:} FPGA Design, Questasim, Quartus II, Spice (Multisim), LabVIEW, MATLAB, Wireshark \\
\textbf{Concepts/Domains:} Computer Architecture, Parallel Computing, Low Power Design, Memory Subsystems, Digital Logic, ML, RTL Design

%-----------EXPERIENCE-----------%
\section*{Work Experience}

\textbf{University of Southern California}, Los Angeles, CA \hfill Jan 2025 -- Jan 2026 \\
\textit{Course Producer (EE354) / Teaching Assistant (EE 457)}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Held office hours and graded assignments for \textbf{Computer Systems Organization} and \textbf{Intro to Digital Circuits}.
    \item Assisted in teaching core concepts like pipelining, cache memory, and digital logic synthesis to undergraduate students.
\end{itemize}

\textbf{Schneider Electric}, Bangalore, India \hfill July 2021 -- Aug 2021 \\
\textit{Intern}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Researched UPS efficiency, proposing improvements for battery longevity and analyzing energy consumption trends.
\end{itemize}

\textbf{Accenture}, Bangalore, India \hfill July 2022 -- Aug 2024 \\
\textit{Backend Developer}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Spearheaded transition to CI/CD pipelines, reducing deployment turnaround time by 50\%.
    \item Developed robust backend services and APIs, ensuring high availability and scalability for critical business applications.
\end{itemize}

%-----------PROJECTS-----------%
\section*{Projects}

\textbf{Microarchitecture Design (EE 457 Course Project)} \hfill 2024 \\
\textit{Verilog, Questasim, Computer Architecture}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Designed and simulated single-cycle CPUs, ALUs, and Tomasulo machines using Verilog and Questasim.
    \item Implemented advanced concepts including register renaming, hazard detection, and out-of-order execution.
\end{itemize}

\textbf{Alarm Clock on FPGA} \hfill 2019 \\
\textit{Verilog, FPGA, Digital Logic}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Built a fully functional alarm clock using Verilog on FPGA hardware, managing display logic, clock cycles, and user input.
    \item Implemented state machines to handle time-setting, alarm triggering, and snoozing functionality suitable for hardware synthesis.
\end{itemize}

\textbf{IoT-Based Keyless Bike Access System} \hfill 2019 \\
\textit{ESP8266, C++, Android, WiFi}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Developed a keyless authentication system using ESP8266 and WiFi for bike access via a mobile app.
    \item Integrated hardware sensors and actuators with low-latency communication protocols.
\end{itemize}

\textbf{TCP/IP Socket Programming (EE 450 Course Project)} \hfill 2025 \\
\textit{C++, Socket Programming, Networking}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Designed and implemented client-server systems for data packet exchange using TCP/IP sockets.
    \item Optimized data transmission protocols for reliability and concurrency.
\end{itemize}

%-----------RESEARCH-----------%
\section*{Research}

\textbf{Learning Optimal Gateway Placement for Low-cost Opportunistic Smart Cities} \hfill 2025 \\
\textit{Network Reconnaissance Lab, USC (Advisor: Professor C. Baker)}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Enhanced placement methodologies and created simulations to realistically model real-world scenarios.
\end{itemize}
\textbf{OpenCV-Based AI-Driven Customer Screening System} \hfill 2024 \\
\textit{Published in Wireless Personal Communications, Springer Journal}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Developed an AI-vision powered system for crowd management using OpenCV \& Machine Learning.
\end{itemize}

%-----------CERTIFICATIONS-----------%
\section*{Certifications \& Awards}
\textbf{Certifications:} MuleSoft Certified Developer (MCD - Level 1) \\
\textbf{Awards:} Pinnacle TCI Award; Growth Catalyst Award (Accenture); National Cyber Olympiad (Zonal Rank 1)

\end{document}
