\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome5}


\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}


% Custom font
\usepackage{mathptmx}


% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{1in}

\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule\vspace{-6pt}]

%Items formatting
\setlist[itemize]{
    leftmargin=2.5em,
    itemsep=2pt,
    topsep=0pt,        % removes space above list
    partopsep=0pt,     % removes extra paragraph spacing
    parsep=0pt         % removes spacing inside items
}

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}}\\
    {\normalsize Software Engineer \textbar\ Backend \& Distributed Systems}\\
    \small
    \faMapMarker*\ Los Angeles, CA
    \quad
    \faPhone*\ +1 323-334-7408
    \quad
    \faEnvelope\ \href{mailto:jaishah.work@gmail.com} {jaishah.work@gmail.com}
    \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/jaishah9} {linkedin.com/in/jaishah9}
\end{center}
\vspace{-13pt}


%-----------EDUCATION-----------%
\section*{Education}
\textbf{University of Southern California (USC)}, Los Angeles, CA \hfill \textbf{Aug 2024 -- May 2026} \\
\textit{Master of Science in Computer Engineering} \hfill GPA: 3.7/4.00 \\
Coursework: Algorithms, Database Management Systems, AI Agents, Programming in Swift, Distributed Systems, Computer Networks.

\vspace{1pt}

\textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill \textbf{Apr 2018 -- May 2022} \\
\textit{B.Tech. in Electronics and Communication (IoT and Sensors)} \hfill GPA: 9.04 / 10.00 \\
Coursework: Object Oriented Programming, Data Structures \& Algorithms, Web Technologies, Cloud Computing.

%-----------EXPERIENCE-----------%
\section*{Work Experience}

\textbf{Software Engineer} \;|\;\hspace{.1cm} \textit{Accenture} \hfill \textbf{Jul 2022 -- Aug 2024} \\

\begin{itemize}[noitemsep]
    \item Designed and deployed automated \textbf{CI/CD pipelines} using \textbf{GitHub Actions} and \textbf{AWS CodePipeline}, reducing release turnaround time by \textbf{70\%} and enabling reliable continuous delivery.
    \item 
    Built and scaled \textbf{30+ RESTful microservices and APIs} supporting backend system design for \textbf{10k+ daily transactions}, improving distributed system integration, scalability, and production reliability.
    \item Defined API architecture with \textbf{OpenAPI 3.0} and implemented centralized \textbf{error handling and fault-tolerance}, reducing debugging time by \textbf{40\%}.
    \item Optimized authentication caching, \textbf{rate limiting}, and performance tuning strategies, increasing overall system throughput by \textbf{25\%}.
\end{itemize}

\textbf{Data Analyst} \;|\; \textit{USC MANN School of Pharmacy} \hfill \textbf{May 2025 -- Present} \\

\begin{itemize}[noitemsep]
    \item Developed \textbf{Tableau + SQL analytics solutions} to transform large-scale datasets into actionable insights, deploying dashboards to on-premise \textbf{Tableau Server} for organization-wide access.
    \item Engineered \textbf{data processing and ETL-style workflows} including cleaning, transformation, and relational joins to support accurate reporting pipelines.
    \item Enhanced \textbf{Salesforce data models} across \textbf{70+ objects} and delivered \textbf{30+ analytical reports} used by \textbf{50+ stakeholders}.
    \item Automated validation and testing using \textbf{Python} and LLM-driven scripts, processing \textbf{100,000+ records} and reducing manual reporting by \textbf{15 hours/week}.
\end{itemize}



%-----------PROJECTS-----------%
\section*{Projects}

\textbf{Healthcare \& Behavioral Insights App} \;|\; \textit{Swift, SwiftUI, CareKit, Docker, PostgreSQL, Heroku} \\
\begin{itemize}[noitemsep]
    \item Developed a native iOS health analytics application using \textbf{CareKit} to capture and analyze longitudinal patient data, integrating task scheduling, outcome tracking, and real-time synchronization.
    \item Built containerized backend services with \textbf{Docker} and \textbf{PostgreSQL}, deploying to \textbf{Heroku} to enable scalable data persistence and secure health record management.
    \item Created interactive visualizations and feedback workflows to surface adherence trends, improving engagement by \textbf{25\%}.
\end{itemize}

\textbf{AadharVision} \;|\; \textit{Python, Flask, OpenCV, Machine Learning, REST APIs} \\
\begin{itemize}[noitemsep]
    \item Engineered a computer-vision–based access management platform using \textbf{Flask} to process real-time occupancy monitoring and identity validation.
    \item Implemented OCR and QR-driven verification pipelines integrated with external APIs, enabling automated authentication and compliance detection with \textbf{OpenCV}.
    \item Optimized backend request handling to support concurrent validation events with low-latency processing.
\end{itemize}

\textbf{Smart Mirror IoT Automation Platform} \;|\; \textit{Python, Raspberry Pi, MQTT, Node-RED, WebSockets} \\
\begin{itemize}[noitemsep]
    \item Architected a distributed IoT system using \textbf{MQTT publish–subscribe messaging} to coordinate communication between edge devices and a central controller.
    \item Developed event-driven automation workflows with \textbf{Node-RED} and Python services to manage device orchestration and sensor integration.
    \item Implemented \textbf{WebSocket-based real-time data streaming} to deliver live telemetry and responsive UI updates.
\end{itemize}

%-----------SKILLS-----------%
\section*{Technical Skills}

\textbf{Programming:} Python, Java, C++, SQL, Swift \\

\textbf{Backend \& Frameworks:} RESTful APIs, Microservices, Distributed Systems, Flask, Node.js, React, SwiftUI, CareKit \\

\textbf{Data \& AI:} DBMS (PostgreSQL, PostGIS, NoSQL) , Data Processing, ML, Computer Vision, LLMs(RAG, AI Agents) \\

\textbf{Cloud \& Tools:} AWS, Docker, CI/CD, Git, GitHub Actions, Tableau, Splunk, Datadog, Postman, MQTT, Node-RED

\end{document}
