\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome5}


\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}


% Custom font
\usepackage{mathptmx}


% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{1in}

\titleformat{\section}{
  \vspace{-12pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule\vspace{-6pt}]

%Items formatting
\setlist[itemize]{
    leftmargin=2.5em,
    itemsep=2pt,
    topsep=0pt,        % removes space above list
    partopsep=0pt,     % removes extra paragraph spacing
    parsep=0pt         % removes spacing inside items
}

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}}\\
    {\normalsize Data Analyst \textbar\ Salesforce Developer \textbar\ CRM \& Business Intelligence Analytics} \\
    \small
    \faMapMarker*\ Los Angeles, CA
    \quad
    \faPhone*\ +1 323-334-7408
    \quad
    \faEnvelope\ \href{mailto:jaishah.work@gmail.com} {jaishah.work@gmail.com}
    \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/jaishah9} {linkedin.com/in/jaishah9}
\end{center}
\vspace{-13pt}

%-------------------- EDUCATION --------------------
\section*{Education}

\textbf{University of Southern California}, \textit{Los Angeles, CA} \hfill Aug 2024 -- May 2026 \\
M.S. Computer Engineering \hfill GPA: 3.7/4.0 \\
Relevant Coursework: Database Management Systems, Distributed Systems, Algorithms, Computer Networks

\vspace{4pt}

\textbf{Vellore Institute of Technology}, \textit{Vellore, India }\hfill Apr 2018 -- May 2022 \\
B.Tech. Electronics \& Communication (IoT \& Sensors) \hfill CGPA: 9.04/10

%-------------------- EXPERIENCE --------------------
\section*{Professional Experience}

\textbf{Data Analyst} – \textit{USC MANN School of Pharmacy} \hfill May 2025 -- Present
\begin{itemize}
\item Developed enterprise analytics dashboards using Tableau and SQL, transforming large datasets into actionable insights for academic and administrative decision-making.
\item Designed ETL-style workflows including data cleaning, transformation, and relational joins to ensure accurate reporting pipelines.
\item Optimized Salesforce environment across 70+ objects and built 30+ analytical reports supporting 50+ stakeholders.
\item Automated validation pipelines using Python to process 100,000+ records, reducing manual reporting by 15 hours/week.
\item Implemented Nintex DocGen automation to streamline document generation and workflow efficiency.
\item Published dashboards to on-prem Tableau Server, improving organization-wide access to real-time analytics.
\end{itemize}

\textbf{Advanced Application Engineer} – \textit{Accenture} \hfill Jul 2022 -- Aug 2024
\begin{itemize}
\item Designed and delivered 30+ API integrations using MuleSoft and Salesforce/APEX supporting 10k+ daily transactions.
\item Built scalable data integration and transformation workflows enabling CRM analytics and system synchronization.
\item Authored OpenAPI specifications and implemented centralized error-handling frameworks, reducing debugging time by 40\%.
\item Engineered CI/CD pipelines using GitHub Actions and AWS CodePipeline, reducing deployment time by 70\%.
\item Integrated monitoring using Splunk and Datadog to ensure data reliability and operational visibility.
\item Worked in Agile development environments contributing to iterative delivery, validation, and system enhancements.
\end{itemize}

%-------------------- PROJECT EXPERIENCE --------------------
\section*{Projects}

\textbf{Healthcare Analytics Application}
\begin{itemize}
\item Designed a longitudinal health-data analytics platform using CareKit to collect, store, and analyze patient-reported outcomes.
\item Built structured data pipelines with PostgreSQL to manage secure ingestion, transformation, and retrieval of health metrics.
\item Developed visualization workflows to identify trends and behavioral insights, increasing user engagement by 25\%.
\end{itemize}


\textbf{AadharVision Data Monitoring Platform}
\begin{itemize}
\item Developed a real-time data aggregation system to track occupancy and compliance metrics using computer vision inputs.
\item Built backend workflows to process OCR-derived identity data and integrate validated records into reporting pipelines.
\item Enabled analytics-driven alerts and monitoring dashboards to support operational decision-making.
\end{itemize}


\textbf{Smart Mirror IoT Analytics Platform}
\begin{itemize}
\item Engineered a real-time data streaming pipeline using MQTT to collect environmental and device telemetry.
\item Designed Node-RED workflows to transform, route, and visualize incoming data for live monitoring dashboards.
\item Built event-driven automation enabling continuous updates and analytics-based notifications.
\end{itemize}



%-------------------- TECHNICAL SKILLS --------------------
\section*{Technical Skills}

\textbf{Data \& Analytics:} SQL, Tableau, ETL Pipelines, Data Visualization, Data Cleaning, Data Validation
 \\
\textbf{Salesforce Ecosystem:} Salesforce CRM, APEX, Workflows, Reporting, Object Modeling, Nintex DocGen \\
\textbf{Integration \& APIs:} MuleSoft, REST APIs, OpenAPI 3.0, DataWeave, API Development \\
\textbf{Programming:} Python, C++, JavaScript \\
\textbf{Platforms \& Tools:} AWS, GitHub Actions, Docker, Splunk, Datadog, Postman, JIRA

%-------------------- CERTIFICATIONS --------------------
\section*{Certification}

MuleSoft Certified Developer (MCD Level 1)

\end{document}
