\documentclass[letterpaper,10pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Custom font
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-8pt}]

%Items formatting
\setlist[itemize]{topsep=0pt}
% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}} \\
    \vspace{2pt}
    \small
    Ph: +1 (323) 334-7408 \quad Email: \href{mailto:jaijayes@usc.edu}{jaijayes@usc.edu} \\
    LinkedIn: \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9} \quad Availability: Earliest possible \\
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------%
\section*{Education}
\textbf{University of Southern California (USC)}, Los Angeles, CA \hfill Aug 2024 -- May 2026 \\
\textit{Master of Science in Computer Engineering} \hfill GPA: 3.7/4.00 \\
Related Coursework: AI Agents, Database Management Systems, Algorithms, Computer Networks, Adv. Architecture.

\vspace{1pt}

\textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill April 2018 -- May 2022 \\
\textit{B.Tech. in Electronics and Communication (IoT and Sensors)} \hfill CGPA: 9.04 / 10.00 \\
Related Coursework: IoT Systems, Object Oriented Programming, Data Structures \& Algorithms, Web Technologies.

%-----------SKILLS-----------%
\section*{Technical Skills}
\textbf{Languages:} Python, Java, C++, JavaScript, SQL, APEX, Verilog, HTML5, CSS3, C, Shell Scripting \\
\textbf{AI \& Automation:} ChatGPT, GitHub Copilot, Antigravity, Vibe Coding, Codex, OpenCV, AI Agents, Machine Learning \\
\textbf{Cloud \& DevOps:} AWS (CodePipeline, CodeBuild, Stacks), CI/CD, Docker, GitHub Actions, JIRA, Linux, Git \\
\textbf{Integration \& IoT:} MuleSoft, RESTful APIs, Salesforce, Tableau, MQTT, ESP8266, Raspberry Pi, Sensors, Wireshark

%-----------EXPERIENCE-----------%
\section*{Work Experience}
\textbf{Accenture}, Bangalore, India \hfill July 2022 -- Aug 2024 \\
\textit{Advanced Application Developer}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-3pt]
    \item Supervised transition from manual deployments to CI/CD pipeline against tight deadlines, reducing turnaround time by 50\% and streamlining Dev-QA handoffs.
    \item Developed and maintained custom CRM applications using Salesforce and APEX; delivered 30+ API services using MuleSoft to serve critical business functions.
    \item Created reusable frameworks for logging and error handling for the company, significantly improving system observability.
    \item Worked closely on various auth token caching and API rate limiting strategies to enhance system security and stability.

\end{itemize}

\textbf{MANN School of Pharmacy (USC)}, Los Angeles, CA \hfill May 2025 -- Present \\
\textit{Data Analyst / Internal Tools Developer}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-3pt]
    \item Managed the Faculty Management System, an internal Salesforce-based application, ensuring data integrity and system availability.
    \item Developed interactive data visualizations using Tableau to provide actionable insights for decision-making.
    \item Assisted in the maintenance and improvement of internal software solutions to support school operations.
\end{itemize}

%-----------PROJECTS-----------%
\section*{Projects}
\textbf{Smart Mirror with MQTT Home Automation} \hfill Raspberry Pi, MQTT, Python
\begin{itemize}[leftmargin=*,noitemsep,topsep=-3pt]
    \item Built a Smart Mirror using Raspberry Pi and ESP8266, integrated with home automation via MQTT to control appliances.
    \item Designed an interactive interface displaying real-time information such as weather, news, and calendar events.
    \item Implemented low-latency communication protocols to ensure seamless control of connected IoT devices.
\end{itemize}

\textbf{Automated Google Form Submission Bot} \hfill Python, Flask
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Developed an internal automation tool using Python and Flask to bulk-fill Google Forms, eliminating repetitive manual entry.
    \item Reduced data processing time by 98\% and achieved near-zero error rates in high-volume submission scenarios.
\end{itemize}

\textbf{Web Scrapers and Automation Suite} \hfill Python, Selenium
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Implemented Selenium-based web scrapers and automation scripts to verify consistency across multiple web platforms.
    \item Built custom tools to automate data collection and validation processes for quality assurance, saving numerous man-hours.
\end{itemize}

\textbf{IoT-Based Keyless Bike Access System} \hfill ESP8266, C++, WiFi
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Built a real-world IoT solution for secure vehicle access using ESP8266 and WiFi, controlled via a custom mobile app.
    \item Integrated hardware sensors with software logic to demonstrate secure, end-to-end system control.
\end{itemize}

\textbf{Microarchitecture Design (EE 457 Course Project)} \hfill Verilog, Simulation
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Designed and simulated complex processor components (ALUs, Tomasulo machines) using Verilog and Questasim.
    \item Identified and resolved architectural hazards through rigorous simulation, optimizing execution cycles.
\end{itemize}

%-----------RESEARCH-----------%
\section*{Research}
\textbf{Learning Optimal Gateway Placement for Low-cost Opportunistic Smart Cities} \hfill 2025 \\
\textit{Network Reconnaissance Lab, USC (Advisor: Professor C. Baker)}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Enhanced placement methodologies and created simulations to realistically model real-world scenarios in distributed networks.
\end{itemize}

\textbf{OpenCV-Based AI-Driven Customer Screening System} \hfill 2024 \\
\textit{Published in Wireless Personal Communications, Springer Journal}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Developed an AI-vision powered system for crowd management using OpenCV \& Machine Learning.
\end{itemize}

%-----------CERTIFICATIONS-----------%
\section*{Certifications \& Awards}
\textbf{Certifications:} MuleSoft Certified Developer (MCD - Level 1) \\
\textbf{Awards:} Pinnacle TCI Award; Growth Catalyst Award (Accenture)

\end{document}
