\documentclass[letterpaper,10pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Custom font
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.85in}
\addtolength{\textheight}{1.7in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

%Items formatting
\setlist[itemize]{topsep=0pt, itemsep=0pt, parsep=0pt, partopsep=0pt}
% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}} \\
    \vspace{5pt}
    \small
    Ph: +1 (323) 334-7408 \quad Email: \href{mailto:jaijayes@usc.edu}{jaijayes@usc.edu} \\
    LinkedIn: \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9} \\
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------%
\section*{Education}
\textbf{University of Southern California (USC)}, Los Angeles, CA \hfill Aug 2024 -- May 2026 \\
\textit{Master of Science in Computer Engineering} \hfill GPA: 3.7/4.00 \\
Related Coursework: Database Management Systems, AI Agents, Algorithms, Computer Networks.

\vspace{2pt}

\textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill April 2018 -- May 2022 \\
\textit{B.Tech. in Electronics and Communication (IoT and Sensors)} \hfill CGPA: 9.04 / 10.00 \\
Related Coursework: IoT Systems, Cloud Computing, Object Oriented Programming, Web Technologies.

%-----------SKILLS-----------%
\section*{Technical Skills}
\textbf{MuleSoft \& Integration:} MuleSoft, Anypoint Studio, CloudHub, RAML, DataWeave, SAPI/PAPI/EAPI, REST/SOAP APIs \\
\textbf{Salesforce:} Apex, Salesforce Admin, SOQL, CRM Development, Salesforce Workflows \\
\textbf{DevOps \& Tools:} AWS (CodePipeline, CodeBuild), CI/CD, Docker, Datadog, SonarQube, Postman, Splunk, Git/GitHub \\
\textbf{Languages \& DBs:} Python, Java, SQL, MySQL, JavaScript, HTML5, CSS3, PHP

%-----------EXPERIENCE-----------%
\section*{Work Experience}
\textbf{Accenture}, Bangalore, India \hfill July 2022 -- Aug 2024 \\
\textit{Backend Developer}
\begin{itemize}
    \item Supervised transition from manual deployments to CI/CD pipeline, reducing turnaround time by \textbf{50\%} and streamlining Dev-QA handoffs.
    \item Created \textbf{2 reusable frameworks} for logging and error handling, reducing debugging time by \textbf{40\%} and preventing system downtime.
    \item Developed and maintained custom CRM applications using Salesforce and APEX; delivered \textbf{30+ end-to-end integrations} and API services handling \textbf{10k+ daily requests}.
    \item Optimized auth token caching and API rate limiting strategies, improving system throughput by \textbf{25\%}.
\end{itemize}

\textbf{University of Southern California}, Los Angeles, CA \hfill Jan 2025 -- Present \\
\textit{Data Analyst, MANN School of Pharmacy} \hfill (May 2025 -- Present)
\begin{itemize}
    \item Optimized Salesforce apps with \textbf{70+ objects} and created \textbf{30+ interactive Tableau reports}, improving data accessibility for \textbf{50+ staff}.
    \item Automated data validation using Python scripts, processing \textbf{100,000+ records} and cutting manual reporting time by \textbf{15 hours/week}.
\end{itemize}

\textit{Teaching Assistant, EE 457 (Computer Systems Organization)} \hfill (Jan 2025 -- Jan 2026)
\begin{itemize}
    \item Assisted Professor Puvvada in revamping assignments and supporting \textbf{100+ students} to improve learning outcomes.
\end{itemize}

%-----------RESEARCH-----------%
\section*{Research}
    \textbf{Learning Optimal Gateway Placement for Low-cost Smart Cities} \hfill USC, 2025
    \begin{itemize}
        \item Enhanced placement methodologies and created simulations to realistically model real-world scenarios.
        \item Presented poster at 14th Annual Electrical Engineering Research Festival, USC.
    \end{itemize}
    
    \textbf{OpenCV-Based AI-Driven Customer Screening System} \hfill Springer Journal, 2024
    \begin{itemize}
        \item Developed an AI-vision powered system for crowd management using OpenCV \& Machine Learning.
        \item Published findings in \textit{Wireless Personal Communications}, DOI: 10.1007/s11277-024-11286-x.
    \end{itemize}

%-----------PROJECTS-----------%
\section*{Projects}
\textbf{Microarchitecture Design (EE 457 Course Project)} \hfill Verilog, Questasim
\begin{itemize}
    \item Designed and simulated single-cycle CPUs, ALUs, and Tomasulo machines using Verilog and Questasim.
    \item Implemented advanced concepts including register renaming, hazard detection, and out-of-order execution.
\end{itemize}

\textbf{Automated Google Form Submission Bot} \hfill Python, Flask
\begin{itemize}
    \item Designed an automation bot using Python (Flask) to bulk-fill Google Forms, optimizing time by 98\% compared to manual entry.
\end{itemize}

\textbf{Web Scrapers and Automation Suite} \hfill Python, Selenium
\begin{itemize}
    \item Implemented Selenium-based test suites to verify feature deployment consistency across multiple user profiles.
\end{itemize}

\textbf{IoT-Based Keyless Bike Access System} \hfill ESP8266, WiFi
\begin{itemize}
    \item Developed a keyless authentication system using ESP8266 and WiFi for bike access via a mobile app.
    \item Facilitated secure vehicle sharing and real-time status tracking for campus mobility.
\end{itemize}

%-----------CERTIFICATIONS & AWARDS-----------%
\section*{Certifications \& Awards}
\begin{itemize} \itemsep -2pt
    \item \textbf{Certifications:} MuleSoft Certified Developer (MCD - Level 1).
    \item \textbf{Awards:} Pinnacle TCI Award, Growth Catalyst Award (Accenture).
    \item \textbf{Workshops:} Tableau Next, Future of Computer Architecture and Hardware Security.
\end{itemize}

\end{document}
