\documentclass[letterpaper,10pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Custom font
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-6pt}]

%Items formatting
\setlist[itemize]{topsep=0pt}
% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}} \\
    \vspace{2pt}
    \small
    Ph: +1 (323) 334-7408 \quad Email: \href{mailto:jaijayes@usc.edu}{jaijayes@usc.edu} \\
    LinkedIn: \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9} \quad Availability: Earliest possible \\
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------%
\section*{Education}
\textbf{University of Southern California (USC)}, Los Angeles, CA \hfill Aug 2024 -- May 2026 \\
\textit{Master of Science in Computer Engineering} \hfill GPA: 3.7/4.00 \\
Related Coursework: Advanced Computer Architecture, Digital Circuits, Computer Networks, Embedded Systems, VLSI.

\vspace{1pt}

\textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill April 2018 -- May 2022 \\
\textit{B.Tech. in Electronics and Communication (IoT and Sensors)} \hfill CGPA: 9.04 / 10.00 \\
Related Coursework: IoT Systems, Microcontrollers, Data Structures \& Algorithms, Object Oriented Programming.

%-----------SKILLS-----------%
\section*{Technical Skills}
\textbf{Languages:} C++, C, Python, MATLAB, Verilog, Bash, JavaScript, SQL, Assembly, SystemVerilog \\
\textbf{Embedded \& Hardware:} Raspberry Pi, ESP8266, FPGA, UART/I2C/SPI, Oscilloscopes, Logic Analyzers \\
\textbf{Development Tools:} Linux, Git, GCC, GitHub Actions, Docker, CI/CD, JIRA, Questasim, Vivado, Keil \\
\textbf{Cloud \& Protocols:} AWS, MQTT, TCP/IP, RESTful APIs, WiFi, Bluetooth, HTTP/HTTPS

%-----------EXPERIENCE-----------%
\section*{Work Experience}
\textbf{University of Southern California}, Los Angeles, CA \hfill Jan 2025 -- Present \\
\textit{Course Producer (Digital Circuits) / Teaching Assistant (Computer Systems Org)}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-3pt]
    \item Assisted in teaching core concepts of digital logic, computer organization, and hardware description languages to roughly 100 students.
    \item Developed strategies to improve student understanding of complex architectural simulations and embedded concepts.
\end{itemize}

\textbf{Accenture}, Bangalore, India \hfill July 2022 -- Aug 2024 \\
\textit{Advanced Application Developer}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-3pt]
    \item Developed high-volume distributed systems, delivering 30+ scalable API services using MuleSoft for enterprise clients.
    \item Supervised transition to automated CI/CD pipelines, ensuring robust software delivery lifecycles and reducing deployment errors.
    \item Created reusable logging and error-handling frameworks to improve system reliability and observability across the team.
\end{itemize}

%-----------PROJECTS-----------%
\section*{Projects}
\textbf{Microarchitecture Design \& Simulation} \hfill Verilog, Questasim
\begin{itemize}[leftmargin=*,noitemsep,topsep=-3pt]
    \item Designed and simulated single-cycle CPUs, ALUs, and Tomasulo machines, implementing deep pipelines and out-of-order execution logic.
    \item Wrote comprehensive test benches to verify logic correctness and resolve hazard detection issues in simulation environments.
\end{itemize}

\textbf{IoT-Based Keyless Bike Access System} \hfill ESP8266, C++, WiFi
\begin{itemize}[leftmargin=*,noitemsep,topsep=-3pt]
    \item Developed firmware for ESP8266 microcontrollers to enable secure, real-time vehicle access via a custom mobile app.
    \item Integrated hardware sensors and actuators (relays, solenoids), optimizing power consumption and signal reliability.
\end{itemize}

\textbf{Smart Mirror with MQTT Home Automation} \hfill Raspberry Pi, Python, Linux
\begin{itemize}[leftmargin=*,noitemsep,topsep=-3pt]
    \item Built a Linux-based smart mirror system integrating hardware displays with cloud-based home automation services via MQTT.
    \item Developed Python scripts for real-time data fetching (weather, news) and signal processing from connected IoT devices.
\end{itemize}

\textbf{Alarm Clock on FPGA} \hfill Verilog, FPGA
\begin{itemize}[leftmargin=*,noitemsep,topsep=-3pt]
    \item Built a fully functional alarm clock using Verilog on FPGA hardware, managing display logic, clock cycles, and user input debouncing.
    \item Implemented finite state machines (FSMs) to handle time-keeping and alarm triggering logic with high precision.
\end{itemize}

\textbf{TCP/IP Socket Programming} \hfill C++, Networking
\begin{itemize}[leftmargin=*,noitemsep,topsep=-3pt]
    \item Implemented low-level client-server communication protocols using C++ sockets, handling concurrency and data packet integrity.
\end{itemize}

%-----------RESEARCH-----------%
\section*{Research}
\textbf{Learning Optimal Gateway Placement for Low-cost Opportunistic Smart Cities} \hfill 2025 \\
\textit{Network Reconnaissance Lab, USC (Advisor: Professor C. Baker)}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-3pt]
    \item Created simulations to model real-world signal propagation and optimize gateway placement in distributed networks.
\end{itemize}

\textbf{OpenCV-Based AI-Driven Customer Screening System} \hfill 2024 \\
\textit{Published in Wireless Personal Communications, Springer Journal}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-3pt]
    \item Developed a computer vision system using Python and OpenCV for real-time signal processing and object detection.
\end{itemize}

%-----------CERTIFICATIONS-----------%
\section*{Certifications \& Awards}
\textbf{Certifications:} MuleSoft Certified Developer (MCD - Level 1) \\
\textbf{Awards:} Pinnacle TCI Award; Growth Catalyst Award (Accenture)

\end{document}
