\documentclass[letterpaper,10pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Custom font
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.85in}
\addtolength{\textheight}{1.7in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

%Items formatting
\setlist[itemize]{topsep=2pt, itemsep=1pt}
% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}} \\
    \vspace{4pt}
    \small
    Ph: +1 (323) 334-7408 \quad Email: \href{mailto:jaijayes@usc.edu}{jaijayes@usc.edu} \\
    LinkedIn: \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9} \\
    \vspace{-10pt}
\end{center}

%-----------EDUCATION-----------%
\section*{Education}
    \textbf{University of Southern California (USC)}, Los Angeles, CA \hfill Aug 2024 -- May 2026 \\
    \textit{Master of Science in Computer Engineering} \hfill GPA: 3.7/4.00 \\
    Relevant Coursework: Computer Networks, Algorithms, AI Agents, Database Management Systems. \\

    \vspace{2pt}
    \textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill April 2018 -- May 2022 \\
    \textit{B.Tech. in Electronics and Communication} \hfill CGPA: 9.04 / 10.00 \\
    Relevant Coursework: IoT Systems, Cloud Computing, Object Oriented Programming, Web Technologies.

%-----------SKILLS-----------%
\section*{Technical Skills}
    \textbf{Languages:} Python, C++, SQL, Bash, Java, JavaScript, HTML5, CSS3, APEX \\
    \textbf{Networking \& OS:} TCP/IP, OSI Model (L1-L3), Wireshark, LAN/WAN, Linux, MQTT, Docker, Network Troubleshooting \\
    \textbf{Cloud \& DevOps:} Ansible, AWS (CodePipeline, CodeBuild), CI/CD, Git, GitHub Actions, Salesforce, MuleSoft \\
    \textbf{Concepts:} Data Structures \& Algorithms, SDLC, RESTful APIs, Agile, Testing \& QA, System Architecture

%-----------EXPERIENCE-----------%
\section*{Work Experience}
    \textbf{Accenture}, Bangalore, India \hfill July 2022 -- Aug 2024 \\
    \textit{Advanced Application Developer}
    \begin{itemize}[leftmargin=*]
        \item Supervised transition from manual deployments to CI/CD pipeline, reducing turnaround time by \textbf{50\%} and streamlining Dev-QA handoffs.
        \item Created \textbf{2 reusable frameworks} for logging and error handling, reducing debugging time by \textbf{40\%} and preventing system downtime.
        \item Developed and maintained custom CRM applications using Salesforce and APEX; delivered \textbf{30+ end-to-end integrations} and API services handling \textbf{10k+ daily requests}.
        \item Optimized auth token caching and API rate limiting strategies, improving system throughput by \textbf{25\%}.
    \end{itemize}

    \vspace{2pt}
    \textbf{University of Southern California}, Los Angeles, CA \hfill Jan 2025 -- Present \\
    \textit{Teaching Assistant, EE 457 (Computer Systems Organization)} \hfill (Jan 2025 -- Jan 2026)
    \begin{itemize}[leftmargin=*]
        \item Assisted Professor Puvvada in revamping assignments and supporting \textbf{100+ students} to improve learning outcomes.
    \end{itemize}

    \textit{Course Producer, EE354 (Intro to Digital Circuits)} \hfill (Aug 2025 -- Jan 2026)
    \begin{itemize}[leftmargin=*]
        \item Held office hours, graded assignments/exams, and managed logistics for a class of \textbf{80+ students}.
    \end{itemize}
    
    \textit{Data Analyst, MANN School of Pharmacy} \hfill (May 2025 -- Present)
    \begin{itemize}[leftmargin=*]
        \item Optimized Salesforce apps with \textbf{70+ objects} and created \textbf{30+ interactive Tableau reports}, improving data accessibility for \textbf{50+ staff}.
        \item Automated data validation using Python scripts, processing \textbf{100,000+ records} and cutting manual reporting time by \textbf{15 hours/week}.
    \end{itemize}

%-----------RESEARCH-----------%
\section*{Research}
    \textbf{Learning Optimal Gateway Placement for Low-cost Smart Cities} \hfill USC, 2025
    \begin{itemize}[leftmargin=*]
        \item Enhanced placement methodologies and created simulations to realistically model real-world scenarios.
        \item Presented poster at 14th Annual Electrical Engineering Research Festival, USC.
    \end{itemize}
    
    \textbf{OpenCV-Based AI-Driven Customer Screening System} \hfill Springer Journal, 2024
    \begin{itemize}[leftmargin=*]
        \item Developed an AI-vision powered system for crowd management using OpenCV \& Machine Learning.
        \item Published findings in \textit{Wireless Personal Communications}, DOI: 10.1007/s11277-024-11286-x.
    \end{itemize}

%-----------PROJECTS-----------%
\section*{Projects}
    \textbf{TCP/IP Socket Programming} \hfill Python, Computer Networks
    \begin{itemize}[leftmargin=*]
        \item Designed and implemented client-server systems for data packet exchange using Python TCP/IP sockets.
    \end{itemize}

    \textbf{Smart Mirror \& Home Automation} \hfill Raspberry Pi, MQTT, IP Protocols
    \begin{itemize}[leftmargin=*]
        \item Built a local area home automation system using MQTT and IP protocols to control appliances with sub-100ms latency.
    \end{itemize}

    \textbf{Web Scrapers and Automation Suite} \hfill Selenium, Python, Automation
    \begin{itemize}[leftmargin=*]
        \item Implemented Selenium-based test suites to verify feature deployment consistency across multiple user profiles.
    \end{itemize}

%-----------CERTIFICATIONS & AWARDS-----------%
\section*{Certifications \& Awards}
    \begin{itemize}[leftmargin=*] \itemsep 0pt
        \item \textbf{MuleSoft Certified Developer (MCD - Level 1)} -- Certified 2023
        \item \textbf{Pinnacle TCI Award (Accenture):} Recognized for exceptional performance (Aug 2023).
        \item \textbf{Growth Catalyst Award (Accenture):} Awarded for outstanding contributions in growth initiatives (June 2023).
    \end{itemize}

\end{document}
