\documentclass[letterpaper,10pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Custom font
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

%Items formatting
\setlist[itemize]{topsep=1.5pt}
% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}} \\
    \vspace{2pt}
    \small
    Ph: +1 (323) 334-7408 \quad Email: \href{mailto:jaijayes@usc.edu}{jaijayes@usc.edu} \\
    LinkedIn: \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9} \\
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------%
\section*{Education}
\textbf{University of Southern California (USC)}, Los Angeles, CA \hfill Aug 2024 -- May 2026 \\
\textit{Master of Science in Computer Engineering} \hfill GPA: 3.7/4.00 \\
Relevant Coursework: Computer Networks, Algorithms, Database Management Systems, AI Agents. \\
\vspace{2pt}
\textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill April 2018 -- May 2022 \\
\textit{B.Tech. in Electronics and Communication} \hfill CGPA: 9.04/10.00 \\
Relevant Coursework: Object Oriented Programming, Web Technologies, Cloud Computing.

%-----------SKILLS-----------%
\section*{Technical Skills}
\textbf{Languages:} Python, Java, SQL, APEX, JavaScript, C++, HTML5, CSS3. \\
\textbf{Frameworks \& Tools:} Flask, MuleSoft, Salesforce (Admin, CRM, Workflows), Node-RED. \\
\textbf{Cloud \& DevOps:} AWS (CodePipeline, CodeBuild), CI/CD pipelines, Git, GitHub Actions, JIRA, Docker. \\
\textbf{Concepts:} RESTful APIs, SDLC, Agile, Data Structures \& Algorithms, Web Scraping.

%-----------EXPERIENCE-----------%
\section*{Work Experience}
\textbf{Accenture}, Bangalore, India \hfill July 2022 -- Aug 2024 \\
\textit{Advanced Application Developer}
\begin{itemize}
    \item Supervised transition from manual deployments to CI/CD pipeline, reducing turnaround time by 50\% and streamlining Dev-QA handoffs.
    \item Developed and maintained custom CRM applications using Salesforce and APEX; delivered 30+ API services using MuleSoft.
    \item Created reusable frameworks for logging and error handling for the company, improving system reliability.
    \item Worked closely on various auth token caching and API rate limiting strategies to optimize performance.
    \item Collaborated with cross-functional teams in an Agile environment to deliver high-quality software solutions.
\end{itemize}

\textbf{University of Southern California}, Los Angeles, CA \hfill May 2025 -- Present \\
\textit{Data Analyst, MANN School of Pharmacy}
\begin{itemize}
    \item Helping build and test custom CRM applications on Salesforce to manage student data effectively.
    \item Creating interactive data visualizations on Tableau to derive actionable insights for the administration.
\end{itemize}

\textbf{University of Southern California}, Los Angeles, CA \hfill Jan 2025 -- Jan 2026 \\
\textit{Teaching Assistant, EE 457 / Course Producer, EE 354}
\begin{itemize}
    \item Assisted professors in revamping assignments and developing strategies to improve student learning outcomes.
    \item Managed logistics, graded assignments, and held office hours to support student success in digital circuits.
\end{itemize}

%-----------PROJECTS-----------%
\section*{Projects}
\textbf{Automated Google Form Submission Bot} \hfill Python, Flask \\
\begin{itemize}
    \item Designed an automation bot using Python (Flask) to bulk-fill Google Forms, optimizing time by 98\% compared to manual entry.
    \item Implemented robust error handling and validation logic to ensure data integrity during submission.
\end{itemize}

\textbf{Web Scrapers and Automation Suite} \hfill Selenium, Python \\
\begin{itemize}
    \item Implemented Selenium-based test suites to verify feature deployment consistency across multiple user profiles.
    \item Automates routine data extraction tasks, significantly reducing manual effort and potential human error.
\end{itemize}

\textbf{TCP/IP Socket Programming} \hfill Python, Networking \\
\begin{itemize}
    \item Designed and implemented client-server systems for data packet exchange using Python TCP/IP sockets.
    \item Demonstrated understanding of reliable data transfer and network protocols.
\end{itemize}



%-----------CERTIFICATIONS & AWARDS-----------%
\section*{Certifications \& Awards}
\begin{itemize} \itemsep -2pt
    \item \textbf{MuleSoft Certified Developer (MCD - Level 1)} -- Certified 2023.
    \item \textbf{Pinnacle TCI Award (Accenture):} Recognized for exceptional performance (Aug 2023).
    \item \textbf{Growth Catalyst Award (Accenture):} Awarded for outstanding contributions in growth initiatives (June 2023).
\end{itemize}

\end{document}
