\documentclass[letterpaper,10pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Custom font
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-6pt}]

%Items formatting
\setlist[itemize]{topsep=0pt}
% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}} \\
    \vspace{2pt}
    \small
    Ph: +1 (323) 334-7408 \quad Email: \href{mailto:jaijayes@usc.edu}{jaijayes@usc.edu} \\
    LinkedIn: \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9} \quad Availability: Earliest possible \\
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------%
\section*{Education}
\textbf{University of Southern California (USC)}, Los Angeles, CA \hfill Aug 2024 -- May 2026 \\
\textit{Master of Science in Computer Engineering} \hfill GPA: 3.7/4.00 \\
Related Coursework: Computer Networks, Database Management Systems, Algorithms, Distributed Systems, Adv. Architecture.

\vspace{2pt}

\textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill April 2018 -- May 2022 \\
\textit{B.Tech. in Electronics and Communication (IoT and Sensors)} \hfill CGPA: 9.04 / 10.00 \\
Related Coursework: IoT Systems, Object Oriented Programming, Data Structures \& Algorithms.

%-----------SKILLS-----------%
\section*{Technical Skills}
\textbf{Languages:} Python, Java, Bash, Shell Scripting, YAML, SQL, JavaScript, C++, HTML5, CSS3, C \\
\textbf{Platform \& DevOps:} AWS (EC2, IAM, stacks), CI/CD Pipelines, Docker, Datadog, Splunk, Linux, Git, Wireshark \\
\textbf{Automation \& AI Tools:} GitHub Copilot, ChatGPT, Codex, Selenium, Vibe Coding, AI Agents, Antigravity \\
\textbf{Integration:} MuleSoft, RESTful APIs, JSON, Postman, MQTT, Salesforce, Tableau

%-----------EXPERIENCE-----------%
\section*{Work Experience}
\textbf{Accenture}, Bangalore, India \hfill July 2022 -- Aug 2024 \\
\textit{Advanced Application Developer}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Supervised transition from manual deployments to CI/CD pipeline, reducing turnaround time by 50\% and streamlining Dev-QA handoffs; ensured safer methods for production.
    \item Created reusable frameworks for logging and error handling, operationalizing standardized patterns across the engineering team.
    \item Implement robust guardrails including auth token caching and API rate limiting strategies to ensure system stability and security.
    \item Delivered 30+ API services using MuleSoft, supporting scalable communication for business-critical applications.
\end{itemize}

\textbf{MANN School of Pharmacy (USC)}, Los Angeles, CA \hfill May 2025 -- Present \\
\textit{Data Analyst / Internal Tools Developer}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Managed the Faculty Management System, an internal application, ensuring system uptime and data integrity for staff.
    \item Developed and maintained internal software solutions utilizing Tableau to streamline administrative workflows and support operations.
\end{itemize}

%-----------PROJECTS-----------%
\section*{Projects}
\textbf{Web Scrapers and Automation Suite} \hfill Python, Selenium
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Implemented automation scripts and test suites to verify deployment consistency across multiple environments.
    \item Built custom internal tooling to automate data collection and validation, significantly reducing manual engineering toil.
\end{itemize}

\textbf{Automated Google Form Submission Bot} \hfill Python, Flask
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Designed an automation bot to bulk-process data entry, demonstrating capability to automate repetitive workflows.
    \item Optimized process time by 98\%, showcasing efficiency improvements through code-based automation.
\end{itemize}

\textbf{TCP/IP Socket Programming (EE 450 Course Project)} \hfill C++, Socket Programming
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Designed client-server architecture for reliable data exchange, optimizing transmission protocols for concurrency.
    \item Gained deep understanding of network layers and distributed system communication (TCP/IP).
\end{itemize}

\textbf{IoT-Based Keyless Bike Access System} \hfill ESP8266, C++, WiFi
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Built an end-to-end IoT system integrating hardware and software for secure access control.
    \item Managed real-time device communication and state management in a distributed environment.
\end{itemize}

\textbf{Smart Mirror with MQTT Home Automation} \hfill Raspberry Pi, MQTT, Python
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Built a Smart Mirror using Raspberry Pi and ESP8266, integrated with home automation via MQTT.
    \item Designed an interactive interface displaying real-time information such as weather and news.
\end{itemize}

%-----------RESEARCH-----------%
\section*{Research}
\textbf{Learning Optimal Gateway Placement for Low-cost Opportunistic Smart Cities} \hfill 2025 \\
\textit{Network Reconnaissance Lab, USC (Advisor: Professor C. Baker)}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Enhanced placement methodologies and created simulations to realistically model real-world scenarios.
\end{itemize}

\textbf{OpenCV-Based AI-Driven Customer Screening System} \hfill 2024 \\
\textit{Published in Wireless Personal Communications, Springer Journal}
\begin{itemize}[leftmargin=*,noitemsep,topsep=-2pt]
    \item Developed an AI-vision powered system for crowd management using OpenCV \& Machine Learning.
\end{itemize}

%-----------CERTIFICATIONS-----------%
\section*{Certifications \& Awards}
\textbf{Certifications:} MuleSoft Certified Developer (MCD - Level 1) \\
\textbf{Awards:} Pinnacle TCI Award; Growth Catalyst Award (Accenture)

\end{document}
