\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome5}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{mathptmx}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{1in}

\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule\vspace{-6pt}]

\setlist[itemize]{
    leftmargin=2.5em,
    itemsep=2pt,
    topsep=0pt,
    partopsep=0pt,
    parsep=0pt
}

\pdfgentounicode=1

\begin{document}

\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}}\\
    {\normalsize Software Engineer \textbar\ Medical AI \& Distributed Systems}\\
    \small
    \faMapMarker*\ Los Angeles, CA
    \quad
    \faPhone*\ +1 323-334-7408
    \quad
    \faEnvelope\ \href{mailto:jaishah.work@gmail.com} {jaishah.work@gmail.com}
    \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/jaishah9} {linkedin.com/in/jaishah9}
\end{center}
\vspace{-13pt}

\section*{Education}
\textbf{University of Southern California (USC)}, Los Angeles, CA \hfill \textbf{Aug 2024 -- May 2026} \\
\textit{Master of Science in Computer Engineering} \hfill GPA: 3.7/4.00 \\
Relevant Coursework: Database Management Systems, AI Agents, Programming in Swift, Distributed Systems, Computer Networks.

\vspace{1pt}

\textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill \textbf{Apr 2018 -- May 2022} \\
\textit{B.Tech. in Electronics and Communication (IoT and Sensors)} \hfill CGPA: 9.04 / 10.00 \\
Relevant Coursework: IoT Systems, Web Technologies, Data Acquisition, Object Oriented Programming.

\section*{Work Experience}
\textbf{Data Analyst} \;|\; \textit{USC MANN School of Pharmacy} \hfill \textbf{May 2025 -- Present} \\
\begin{itemize}[noitemsep]
    \item Developed \textbf{Tableau + SQL analytics solutions} to transform large-scale datasets into actionable insights, deploying dashboards to on-premise \textbf{Tableau Server}.
    \item Engineered \textbf{data processing and ETL-style workflows} including cleaning, transformation, and relational joins to support accurate reporting pipelines.
    \item Automated validation and testing using \textbf{Python} and LLM-driven scripts, processing \textbf{100,000+ records} and reducing manual reporting by \textbf{15 hours/week}.
\end{itemize}

\textbf{Software Engineer} \;|\; \textit{Accenture} \hfill \textbf{Jul 2022 -- Aug 2024} \\
\begin{itemize}[noitemsep]
    \item Built and scaled \textbf{30+ RESTful microservices and APIs} supporting backend system design for \textbf{10k+ daily transactions}, improving scalability and reliability.
    \item Designed and deployed automated \textbf{CI/CD pipelines} using \textbf{GitHub Actions} and \textbf{AWS CodePipeline}, reducing release turnaround time by \textbf{70\%}.
    \item Optimized authentication caching, \textbf{rate limiting}, and performance tuning, increasing overall system throughput by \textbf{25\%}.
    \item Implemented monitoring using \textbf{Splunk and Datadog} to ensure data reliability and operational visibility in a regulated environment.
\end{itemize}

\section*{Projects}
\textbf{Healthcare \& Behavioral Insights App} \;|\; \textit{Swift, CareKit, Docker, PostgreSQL} \\
\begin{itemize}[noitemsep]
    \item Developed a native iOS health analytics application using \textbf{CareKit} to capture and analyze longitudinal patient data, integrating task scheduling and outcome tracking.
    \item Built containerized backend services with \textbf{Docker} and \textbf{PostgreSQL} to enable scalable data persistence and secure medical health record management.
\end{itemize}

\textbf{AadharVision} \;|\; \textit{Python, Flask, OpenCV, Machine Learning} \\
\begin{itemize}[noitemsep]
    \item Engineered a computer-vision–based platform using \textbf{OpenCV} and \textbf{Flask} to process real-time identity validation and compliance detection.
    \item Implemented OCR-driven verification pipelines integrated with external APIs, enabling automated authentication and secure data processing.
\end{itemize}

\section*{Technical Skills}
\textbf{Languages:} Python, SQL, C++, Swift, JavaScript, Java \\
\textbf{Data \& AI:} Deep Learning Models, Machine Learning, Computer Vision, ETL Pipelines, RAG/LLMs, Tableau, NoSQL \\
\textbf{Backend \& Tools:} RESTful APIs, Flask, Docker, PostgreSQL, CI/CD, AWS, GitHub Actions, Git, Linux \\

\textit{Note: Would you like to add experience with HIPAA-compliant data handling or R (statistical programming) to your resume to better align with the clinical requirements of the UCSF role?}

\end{document}