\documentclass[letterpaper,11pt]{article}
\usepackage{fontawesome5}


\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}


% Custom font
\usepackage{mathptmx}


% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{1in}

\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule\vspace{-6pt}]

%Items formatting
\setlist[itemize]{
    leftmargin=2.5em,
    itemsep=2pt,
    topsep=0pt,        % removes space above list
    partopsep=0pt,     % removes extra paragraph spacing
    parsep=0pt         % removes spacing inside items
}

% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}}\\
    {\normalsize Application Programmer | Medical AI Software Engineer}\\
    \small
    \faMapMarker*\ Los Angeles, CA
    \quad
    \faPhone*\ +1 323-334-7408
    \quad
    \faEnvelope\ \href{mailto:jaishah.work@gmail.com}{jaishah.work@gmail.com}
    \quad
    \faLinkedin\ \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9}
\end{center}
\vspace{-13pt}


%-----------EDUCATION-----------%
\section*{Education}
\textbf{University of Southern California (USC)}, Los Angeles, CA \hfill 2024 -- 2026 \\
\textit{Master of Science in Computer Engineering} \hfill GPA: 3.7/4.00 \\
Relevant Coursework: Database Management Systems, AI Agents, Algorithms, Distributed Systems, Computer Networks. \\
\textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill 2018 -- 2022 \\
\textit{B.Tech. in Electronics and Communication (IoT and Sensors)} \hfill CGPA: 9.04 / 10.00 \\
Relevant Coursework: IoT Systems, Web Technologies, Data Acquisition, Object Oriented Programming, Advanced Microcontrollers.

%-----------EXPERIENCE-----------%
\section*{Work Experience}
\textbf{University of Southern California}, Los Angeles, CA \hfill May 2025 -- Present \\
\textit{Data Analyst, MANN School of Pharmacy}
\begin{itemize}
    \item Developed Tableau + SQL analytics solutions to transform large-scale datasets into actionable insights, deploying dashboards to on-premise Tableau Server.
    \item Engineered data processing and ETL-style workflows including cleaning, transformation, and relational joins to support accurate reporting pipelines.
    \item Enhanced Salesforce data models across 70+ objects and delivered 30+ analytical reports used by 50+ stakeholders.
    \item Automated validation and testing using Python and LLM-driven scripts, processing 100,000+ records and reducing manual reporting by 15 hours/week.
\end{itemize}
\textbf{Accenture}, Bangalore, India \hfill July 2022 -- Aug 2024 \\
\textit{Software Engineer / Advanced Application Engineer}
\begin{itemize}
    \item Built and scaled 30+ RESTful microservices and APIs supporting backend system design for 10k+ daily transactions.
    \item Designed and deployed automated CI/CD pipelines using GitHub Actions and AWS CodePipeline, reducing release turnaround time by 70\%.
    \item Defined API architecture with OpenAPI 3.0 and implemented centralized error handling and fault-tolerance, reducing debugging time by 40\%.
    \item Optimized authentication caching, rate limiting, and performance tuning strategies, increasing overall system throughput by 25\%.
\end{itemize}

%-----------PROJECTS-----------%
\section*{Projects}
\textbf{Healthcare \& Behavioral Insights App} \hfill 2026 \\
\textit{Swift, CareKit, Docker, PostgreSQL, Python}
\begin{itemize}
    \item Developed a native iOS health analytics application using CareKit to capture and analyze longitudinal patient data, integrating task scheduling and outcome tracking.
    \item Built containerized backend services with Docker and PostgreSQL, deploying to Heroku to enable scalable data persistence and secure health record management.
\end{itemize}
\textbf{AadharVision} \hfill 2021 \\
\textit{Flask, OpenCV, Python}
\begin{itemize}
    \item Engineered a computer-vision–based access management platform using Flask to process real-time occupancy monitoring and identity validation.
    \item Implemented OCR and QR-driven verification pipelines integrated with external APIs, enabling automated authentication and compliance detection.
\end{itemize}

%-----------SKILLS-----------%
\section*{Technical Skills}
\textbf{Languages:} Python, SQL, JavaScript, Swift, C, C++, Java, R. \\
\textbf{AI/ML/Data:} Machine Learning, Deep Learning, Computer Vision, RAGs, LLMs, PostgreSQL, NoSQL, Tableau. \\
\textbf{Development:} Flask, React, Node.js, Docker, CI/CD, AWS, Salesforce, RESTful APIs, Git. \\
\textbf{Embedded/IoT:} IoT Systems, Raspberry Pi, ESP8266, MQTT, Sensor Integration.

%-----------RESEARCH-----------%
\section*{Research}
\textbf{Network Reconnaissance Lab, USC} \hfill Aug 2025 -- Dec 2025 \\
Modeled networked embedded systems to evaluate gateway placement strategies minimizing latency and infrastructure cost; presented findings at USC’s Electrical Engineering Research Festival.

\end{document}