\documentclass[letterpaper,10pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% Custom font
\usepackage[default]{lato}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins (Matched to template1.tex)
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting (Matched to template1.tex)
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

%Items formatting (Matched to template1.tex)
\setlist[itemize]{topsep=1.5pt}
% Ensure that generated PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------%
% Resume Content Starts Here
\begin{document}

%----------HEADING----------%
\begin{center}
    {\LARGE \textbf{Jai Jayesh Shah}} \\
    \vspace{5pt}
    \small
    Ph: +1 (323) 334-7408 \quad Email: \href{mailto:jaijayes@usc.edu}{jaijayes@usc.edu} \\
    LinkedIn: \href{https://www.linkedin.com/in/jaishah9}{linkedin.com/in/jaishah9} \quad Availability: Earliest possible \\
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------%
\section*{Education}
\textbf{University of Southern California (USC)}, Los Angeles, CA \hfill Aug 2024 -- May 2026 \\
\textit{Master of Science in Computer Engineering} \hfill GPA: 3.7/4.00 \\
Related Coursework: Computer Networks, Database Management Systems, Algorithms, AI Agents.

\vspace{1pt}

\textbf{Vellore Institute of Technology (VIT)}, Vellore, India \hfill April 2018 -- May 2022 \\
\textit{B.Tech. in Electronics and Communication (IoT and Sensors)} \hfill CGPA: 9.04 / 10.00 \\
Related Coursework: Data Structures \& Algorithms, Object Oriented Programming, IoT Systems.

%-----------SKILLS-----------%
\section*{Technical Skills}
\textbf{Languages:} Python, Java, SQL, C++, JavaScript, HTML5, CSS3, Bash \\
\textbf{Infrastructure \& Cloud:} AWS (CodePipeline, CodeBuild, Stacks), CI/CD pipelines, Docker, Linux \\
\textbf{Integration \& Data:} MuleSoft, RESTful APIs, MQTT, Splunk, Datadog, Tableau \\
\textbf{Tools \& AI:} GitHub, JIRA, Postman, ChatGPT, GitHub Copilot

%-----------EXPERIENCE-----------%
\section*{Work Experience}
\textbf{Accenture}, Bangalore, India \hfill July 2022 -- Aug 2024 \\
\textit{Advanced Application Developer}
\begin{itemize}[leftmargin=*,noitemsep]
    \item Supervised transition from manual deployments to CI/CD pipeline, reducing turnaround time by 50\% and streamlining Dev-QA handoffs.
    \item Developed and maintained custom CRM applications using Salesforce and APEX; delivered 30+ API services using MuleSoft.
    \item Created resuable frameworks for logging and error handling for the company.
    \item Worked closely on various auth token caching and API rate limiting strategies.
\end{itemize}

\vspace{4pt}

\textbf{MANN School of Pharmacy (USC)}, Los Angeles, CA \hfill May 2025 -- Present \\
\textit{Data Analyst}
\begin{itemize}[leftmargin=*,noitemsep]
    \item Helped build and test custom CRM applications on Salesforce and created data visualizations on Tableau.
    \item Wrote various scripts to automate data collection and validation, significantly reducing manual effort
\end{itemize}

%-----------PROJECTS-----------%
\section*{Projects}
\textbf{TCP/IP Socket Programming (EE 450 Course Project)} \hfill Python, TCP/IP
\begin{itemize}[leftmargin=*,noitemsep]
    \item Designed and implemented client-server systems for data packet exchange using Python TCP/IP sockets.
\end{itemize}

\vspace{4pt}

\textbf{Web Scrapers and Automation Suite} \hfill Python, Selenium
\begin{itemize}[leftmargin=*,noitemsep]
    \item Implemented Selenium-based test suites to verify feature deployment consistency across multiple user profiles.
\end{itemize}

\vspace{4pt}

\textbf{Automated Google Form Submission Bot} \hfill Python, Flask
\begin{itemize}[leftmargin=*,noitemsep]
    \item Designed an automation bot using Python (Flask) to bulk-fill Google Forms, optimizing time by 98\% compared to manual entry.
\end{itemize}

\vspace{4pt}

\textbf{IoT-Based Keyless Bike Access System} \hfill ESP8266, C++, WiFi
\begin{itemize}[leftmargin=*,noitemsep]
    \item Developed a keyless authentication system using ESP8266 and WiFi for bike access via a mobile app, facilitating secure vehicle sharing.
\end{itemize}

%-----------RESEARCH-----------%
\section*{Research}
\textbf{Learning Optimal Gateway Placement for Low-cost Opportunistic Smart Cities} \hfill 2025 \\
\textit{Network Reconnaissance Lab, USC (Advisor: Professor C. Baker)}
\begin{itemize}[leftmargin=*,noitemsep]
    \item Enhanced placement methodologies and created simulations to realistically model real-world scenarios.
\end{itemize}

\vspace{4pt}

\textbf{OpenCV-Based AI-Driven Customer Screening System} \hfill 2024 \\
\textit{Published in Wireless Personal Communications, Springer Journal}
\begin{itemize}[leftmargin=*,noitemsep]
    \item Developed an AI-vision powered system for crowd management using OpenCV \& Machine Learning.
\end{itemize}

%-----------CERTIFICATIONS-----------%
\section*{Certifications \& Awards}
\textbf{Certifications:} MuleSoft Certified Developer (MCD - Level 1) \\
\textbf{Awards:} Pinnacle TCI Award; Growth Catalyst Award (Accenture)

\end{document}
